---
title: "Accuracies"
author: "Veronica"
date: "27-Feb-2026"
output: 
  html_document:
    toc: true
---

One common measure from LWL times is accuracy which is measured as the proportion of the time the child is looking at the target out of the time they are looking at either the distractor or the target. 

The data-processing decision is what that window should be -- when should it start and when should it end. (Other questions about whether to baseline-correct and whether to do exclusions based on amount of data covered in later notebooks). 

```{r, echo=F, include=F}
knitr::opts_chunk$set(warning=F, message=F, echo=F)
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))


d_aoi <- readRDS(here("cached_intermediates", "0_d_aoi.rds"))
t_increment <- 200
```


```{r}
datasets <- d_aoi |> select(trial_id, dataset_name, administration_id, subject_id) |> distinct() 

datasets |> distinct(dataset_name)

datasets |> distinct(administration_id)

datasets |> distinct(trial_id)

cdi_data <- readRDS(here("cached_intermediates", "0_cdi_subjects.rds"))

```

how much data do we have?




```{r}
#looks like all datasets have lots of trials
d_aoi |> filter(!is.na(correct)) |> group_by(dataset_name, t_norm)|> tally() |>  ggplot(aes(x=t_norm, y=n, fill=dataset_name, color=dataset_name))+geom_col()+facet_wrap(~dataset_name, scales="free_y")+theme(legend.position = "none")

```

# Data prep

## No boot ICC
```{r, eval=F}
icc_window_sim <- function(t_start = -500, t_end = 4000, object) {
  print(paste(t_start, t_end))

  df <- d_aoi |>
    filter(t_norm > t_start, t_norm < t_end) |>
    group_by(dataset_name, dataset_id, administration_id, target_label, trial_id) |>
    summarise(
      accuracy = mean(correct, na.rm = TRUE),
      prop_data = mean(!is.na(correct))
    ) |>
    filter(!is.na(accuracy)) |> 
    group_by(dataset_name, dataset_id, administration_id, target_label) |>
    mutate(repetition = row_number())

  # compute ICCs
  df |>
    group_by(dataset_name) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c())
}

acc_params <- expand_grid(
  t_start = seq(-1000, 1500, t_increment),
  t_end = seq(2000, 4000, t_increment),
  object = c("administration")
)


tic()
accs <- acc_params |>
  mutate(icc = pmap(list(t_start, t_end, object), icc_window_sim)) |>
  unnest(col = icc)
toc()

saveRDS(accs, here("cached_intermediates", "1_acc_icc_noboot.rds"))
```

and by age

```{r, eval=F}
#admins/dataset in each agebin
d_aoi |> filter(!is.na(correct)) |> distinct(administration_id, age, dataset_name) |>    mutate(age_bin = case_when(
  age< 18 ~ "<18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age>=36~ ">=36")) |>
group_by(dataset_name, age_bin) |> ggplot(aes(x=age_bin, fill=dataset_name))+geom_histogram(stat="count")


d_aoi |> filter(!is.na(correct)) |> distinct(administration_id, age, dataset_name) |>    mutate(age_bin = case_when(
  age< 18 ~ "<18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age>=36~ ">=36")) |>
group_by(dataset_name, age_bin) |> tally() |> arrange(n)

# apply a cutoff of at least 5 kids going into an age-bin x paper

age_bin_cutoff <-d_aoi |> filter(!is.na(correct)) |> distinct(administration_id, age, dataset_name) |>    mutate(age_bin = case_when(
  age< 18 ~ "<18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age>=36~ ">=36")) |>
group_by(dataset_name, age_bin) |> mutate(count=n()) |> filter(count>=5) |> ungroup()

```

```{r, eval=F}
icc_window_sim_age <- function(t_start = -1000, t_end = 4000, object) {
  df <- d_aoi |> inner_join(age_bin_cutoff) |> 
    filter(t_norm > t_start, t_norm < t_end) |>
    group_by(
      dataset_name, dataset_id, age_bin, administration_id,
      target_label, trial_id
    ) |>
    summarise(
      accuracy = mean(correct, na.rm = TRUE),
      prop_data = mean(!is.na(correct))
    ) |> 
    filter(!is.na(accuracy)) |> 
    group_by(dataset_name, age_bin, dataset_id, administration_id, target_label) |>
    mutate(repetition = row_number())

  # compute ICCs
  df |>
    group_by(dataset_name, age_bin) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c())
}

t_increment <- 200

acc_params <- expand_grid(
  t_start = seq(-1000, 1500, t_increment),
  t_end = seq(2000, 4000, t_increment),
  object = c("administration")
)


accs_byage <- acc_params |>
  mutate(icc = pmap(list(t_start, t_end, object), icc_window_sim_age)) |>
  unnest(col = icc)

saveRDS(accs_byage, here("cached_intermediates", "1_acc_icc_noboot_byage.rds"))

```

## Scripts

```{r, eval=F}
source(here("scripts/1_acc_icc_boot.R"))
source(here("scripts/1_acc_cdi_boot.R"))
source(here("scripts/1_acc_test_retest_boot.R"))

```

# Visualizations

## Heatmap noboot ICC

```{r}
icc_noboot <- readRDS(here("cached_intermediates", "1_acc_icc_noboot.rds"))

icc_noboot_summary <- icc_noboot |>
  group_by(t_start, t_end) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  mutate(window_size = t_end - t_start)


ggplot(icc_noboot_summary, aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c(-1000, -500, 0, 500, 1000, 1500)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

ggplot(
  icc_noboot_summary,
  aes(color = mean_icc)
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_segment(aes(x = t_start, xend = t_end, y = mean_icc, yend = mean_icc)) +
  geom_segment(aes(x = t_start, xend = t_start, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  geom_segment(aes(x = t_end, xend = t_end, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  scale_color_viridis(name = "Mean ICC", direction = -1) +
  theme(legend.position = "none") +
  ylab("Mean ICC") +
  xlab("Analysis Window (in ms)")
```

For datasets with data up to at least 3800
```{r}
long_datasets <- d_aoi |> group_by(dataset_name) |> summarize(min_t_norm=min(t_norm), max_t_norm=max(t_norm), count_0=sum(t_norm==0), count_2000=sum(t_norm==2000), count_3800=sum(t_norm==3800)) |> filter(min_t_norm<=0, max_t_norm>=2000) |> filter(count_0/count_2000>.8) |> filter(count_3800/count_2000>.8)

long_datasets
```


```{r}
icc_noboot |> semi_join(long_datasets) |> group_by(t_start, t_end) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  filter(t_start>=0) |> 
  mutate(window_size = t_end - t_start) |> 
  ggplot(aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c( 0, 500, 1000, 1500)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

icc_noboot |> semi_join(long_datasets) |> group_by(t_start, t_end, dataset_name) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  group_by(dataset_name) |> 
  mutate(relative=mean_icc/max(mean_icc),
         relative2=mean_icc-max(mean_icc)) |> 
  filter(t_start>=0, t_start<800) |> 
  mutate(window_size = t_end - t_start) |> 
  ggplot(aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c( 0, 500, 1000, 1500)) +
  facet_wrap(~dataset_name)+
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

```



```{r}
icc_noboot_byage <- readRDS(here("cached_intermediates", "1_acc_icc_noboot_byage.rds"))

icc_noboot_byage_summary <- icc_noboot_byage |>
  group_by(t_start, t_end, age_bin) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  mutate(window_size = t_end - t_start)


ggplot(icc_noboot_byage_summary, aes(x = t_start, y = t_end, fill = mean_icc)) +
  facet_wrap(~age_bin)+
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c(-1000, -500, 0, 500, 1000, 1500)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

ggplot(
  icc_noboot_byage_summary,
  aes(color = mean_icc)
) +
  facet_wrap(~age_bin)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_segment(aes(x = t_start, xend = t_end, y = mean_icc, yend = mean_icc)) +
  geom_segment(aes(x = t_start, xend = t_start, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  geom_segment(aes(x = t_end, xend = t_end, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  scale_color_viridis(name = "Mean ICC", direction = -1) +
  theme(legend.position = "none") +
  ylab("Mean ICC") +
  xlab("Analysis Window (in ms)")
```

## Bootstrapped ICC


```{r}
acc_boot <- readRDS(here("cached_intermediates/1_acc_icc_boot.rds"))
```




```{r}
acc_boot |> ggplot(aes(x = t_start, y = est, ymin = lower, ymax = upper, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 25)) +
  facet_wrap(~dataset_name)+theme(legend.position = "bottom")
```
this is pretty hard to interpret, so we calculate meta-analytic means and ranges for each condition. 

```{r}
library(metafor)
acc_boot_summary <- acc_boot |>
  filter(!is.na(lower), !is.na(upper)) |>
  mutate(
    stdev = (upper - lower) / (1.96 * 2),
    var = stdev**2
  ) |>
  group_by(t_start, t_end) |>
  nest() |>
  mutate(icc = map(data, \(d){
    rma(d$est, d$var) |>
      summary() |>
      coef()
  })) |>
  select(-data) |>
  unnest(icc)


acc_boot_summary_long <- acc_boot |> semi_join(long_datasets) |> 
  filter(!is.na(lower), !is.na(upper)) |>
  mutate(
    stdev = (upper - lower) / (1.96 * 2),
    var = stdev**2
  ) |>
  group_by(t_start, t_end) |>
  nest() |>
  mutate(icc = map(data, \(d){
    rma(d$est, d$var) |>
      summary() |>
      coef()
  })) |>
  select(-data) |>
  unnest(icc)
```

Looking overall

```{r}
acc_boot_summary |> ggplot(aes(x = t_start, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 25))

acc_boot_summary_long |> ggplot(aes(x = t_start, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 25))
```
### by age

```{r}
acc_boot_age <- readRDS(here("cached_intermediates/1_acc_icc_boot_byage.rds"))
acc_boot_age_summary <- acc_boot_age |> 
  filter(!is.na(lower), !is.na(upper)) |>
  mutate(
    stdev = (upper - lower) / (1.96 * 2),
    var = stdev**2
  ) |>
  group_by(t_start, t_end, age_bin) |>
  nest() |>
  mutate(icc = map(data, \(d){
    rma(d$est, d$var) |>
      summary() |>
      coef()
  })) |>
  select(-data) |>
  unnest(icc)

```


```{r}
acc_boot_age_summary |> ggplot(aes(x = t_start, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 50))+facet_wrap(~age_bin, scales="free_y")+theme(legend.position = "bottom")

```


## CDI corr

Reliability measures like ICC tell us how consistently we're measuring *something*, but they don't tell us what the *something* we're measuring is. For that, we want a check on validity, so we look at the correlation between accuracy (measured on different windows) with each of CDI production measures, CDI comprehension measures, and age. 



```{r}
accs_cdi <- readRDS(here("cached_intermediates", "1_acc_cdi_boot.rds"))
```


```{r}
library(metafor)

accs_cdi_summ <-  accs_cdi |> 
  mutate(
    comp_stdev = (comp_upper - comp_lower) / (1.96 * 2),
    comp_var = comp_stdev**2,
    prod_stdev = (prod_upper - prod_lower) / (1.96 * 2),
    prod_var = prod_stdev**2,
    age_stdev = (age_upper - age_lower) / (1.96 * 2),
    age_var = age_stdev**2
  ) |>
  group_by(t_start, t_end) |>
  nest() |>
  mutate(comp= map(data, \(d){
    rma(d$comp_est, d$comp_var) |>
      summary() |>
      coef()
  }),
  prod= map(data, \(d){
    rma(d$prod_est, d$prod_var) |>
      summary() |>
      coef()
  }),
  age= map(data, \(d){
    rma(d$age_est, d$age_var) |>
      summary() |>
      coef()
  })) |>
  select(-data) |>
  unnest(c(comp, prod, age), names_sep="_")


accs_cdi_summ_long <-  accs_cdi |> semi_join(long_datasets) |> 
  mutate(
    comp_stdev = (comp_upper - comp_lower) / (1.96 * 2),
    comp_var = comp_stdev**2,
    prod_stdev = (prod_upper - prod_lower) / (1.96 * 2),
    prod_var = prod_stdev**2,
    age_stdev = (age_upper - age_lower) / (1.96 * 2),
    age_var = age_stdev**2
  ) |>
  group_by(t_start, t_end) |>
  nest() |>
  mutate(comp= map(data, \(d){
    rma(d$comp_est, d$comp_var) |>
      summary() |>
      coef()
  }),
  prod= map(data, \(d){
    rma(d$prod_est, d$prod_var) |>
      summary() |>
      coef()
  }),
  age= map(data, \(d){
    rma(d$age_est, d$age_var) |>
      summary() |>
      coef()
  })) |>
  select(-data) |>
  unnest(c(comp, prod, age), names_sep="_")
```


Correlation with production

```{r}
accs_cdi_summ |> ggplot(aes(x = t_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi_summ_long |> ggplot(aes(x = t_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi |> filter(!is.na(prod_est)) |>  ggplot(aes(x = t_start, y = prod_est, ymin=prod_lower, ymax=prod_upper,  col=as.character(t_end))) +
  geom_pointrange(position=position_dodge(width=50)) +
  coord_flip() +
  theme(legend.position = "none") +
  facet_wrap(~dataset_name)
```
All of these show the expected positive correlation between CDI production and accuracy. Kids who say more words are more accurate.
Correlation with comprehension

```{r}
accs_cdi_summ |> ggplot(aes(x = t_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi_summ_long |> ggplot(aes(x = t_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi |> filter(!is.na(comp_est)) |>  ggplot(aes(x = t_start, y = comp_est, ymin=comp_lower, ymax=comp_upper,  col=as.character(t_end))) +
  geom_pointrange() +
  coord_flip() +
  theme(legend.position = "none") +
  facet_wrap(~dataset_name)
```
Looking at comprehension, there aren't big differences, but we see higher correlations with shorter windows (peaking starting at 400ms). For long windows, peak seems to be for really long like 0-4000ms. 
Again, correlation is positive, as expected!


Correlation with age

Correlating with age isn't a validity check per se, so much as a "if it doesn't correlate with age, we worry" check. 

```{r}
accs_cdi_summ |> ggplot(aes(x = t_start, y = age_estimate, ymin=age_ci.lb, ymax=age_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi_summ_long |> ggplot(aes(x = t_start, y = age_estimate, ymin=age_ci.lb, ymax=age_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi|> filter(!is.na(age_est)) |>  ggplot(aes(x = t_start, y = age_est, ymin=age_lower, ymax=age_upper,  col=as.character(t_end))) +
  geom_pointrange() +
  coord_flip() +
  geom_hline(yintercept=0)+
  theme(legend.position = "none") +
  facet_wrap(~dataset_name)
```
Overall, there is a positive correlation with age that is not very effected by windowing choices. 

### by age TODO
Reliability measures like ICC tell us how consistently we're measuring *something*, but they don't tell us what the *something* we're measuring is. For that, we want a check on validity, so we look at the correlation between accuracy (measured on different windows) with each of CDI production measures, CDI comprehension measures, and age. 



```{r}
accs_cdi_byage <- readRDS(here("cached_intermediates", "1_acc_cdi_boot_byage.rds"))
```


```{r}
library(metafor)

safe_rma <- possibly(\(est, var) {
  rma(est, var) |> summary() |> coef()
}, otherwise = NULL)

accs_cdi_summ_age <-  accs_cdi_byage |> 
  mutate(
    comp_stdev = (comp_upper - comp_lower) / (1.96 * 2),
    comp_var = comp_stdev**2,
    prod_stdev = (prod_upper - prod_lower) / (1.96 * 2),
    prod_var = prod_stdev**2,
    age_stdev = (age_upper - age_lower) / (1.96 * 2),
    age_var = age_stdev**2
  ) |>
  group_by(t_start, t_end, age_bin) |>
  nest() |>
  mutate(comp= map(data, \(d){
    safe_rma(d$comp_est, d$comp_var) 
  }),
  prod= map(data, \(d){
   safe_rma(d$comp_est, d$comp_var)
  }),
  age= map(data, \(d){
    safe_rma(d$age_est, d$age_var) 
  })) |>
  select(-data) |>
  unnest(c(comp, prod, age), names_sep="_")

```


Correlation with production

```{r}
accs_cdi_summ_age |> ggplot(aes(x = t_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~age_bin)

accs_cdi_byage |> filter(!is.na(prod_est)) |> filter(age_bin=="<18") |>  ggplot(aes(x = t_start, y = prod_est, ymin=prod_lower, ymax=prod_upper,  col=as.character(t_end))) +
  geom_pointrange(position=position_dodge(width=50)) +
  coord_flip() +
  theme(legend.position = "none") +
  facet_wrap(age_bin~dataset_name)
```
All of these show the expected positive correlation between CDI production and accuracy. Kids who say more words are more accurate.
Correlation with comprehension

```{r}
accs_cdi_summ_age |> ggplot(aes(x = t_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~age_bin)

```
Looking at comprehension, there aren't big differences, but we see higher correlations with shorter windows (peaking starting at 400ms). For long windows, peak seems to be for really long like 0-4000ms. 
Again, correlation is positive, as expected!


Correlation with age

Correlating with age isn't a validity check per se, so much as a "if it doesn't correlate with age, we worry" check. 

```{r}
accs_cdi_summ_age |> ggplot(aes(x = t_start, y = age_estimate, ymin=age_ci.lb, ymax=age_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~age_bin)

```
Overall, there is a positive correlation with age that is not very effected by windowing choices. 


## Test retest


```{r}
accs_kid_test_retest <- readRDS(here("cached_intermediates", "1_acc_test_retest_boot.rds"))

library(metafor)
accs_kid_test_retest_summ <-  accs_kid_test_retest |>
  mutate(
    stdev = (upper - lower) / (1.96 * 2),
    var = stdev**2,
  ) |>
  group_by(t_start, t_end) |>
  nest() |>
  mutate(corr= map(data, \(d){
    rma(d$est, d$var) |>
      summary() |>
      coef()
  })) |> 
  unnest(corr)
```


```{r}
accs_kid_test_retest |> ggplot(aes(x=t_start, y=est, ymin=lower, ymax=upper, color=as.character(t_end)))+geom_pointrange(position = position_dodge(width=50))+facet_wrap(~dataset_name)+geom_hline(yintercept=0)
```


```{r}
accs_kid_test_retest_summ |> ggplot(aes(x=t_start, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(t_end)))+geom_pointrange(position = position_dodge(width=50))+geom_hline(yintercept=0)

```




# how much t/d looking on longer places (and in what datasets)

```{r}
d_aoi |> group_by(dataset_name, t_norm) |> mutate(has_data=aoi %in% c("target", "distractor")) |> 
  summarize(s=sum(has_data),
            n=n()) |> 
  ggplot(aes(x=t_norm, y=n))+geom_col(fill="blue")+facet_wrap(~dataset_name, scales="free_y") +
  coord_cartesian(xlim=c(0,4050))+geom_vline(xintercept=3800)

d_aoi |> group_by(dataset_name, t_norm) |> mutate(has_data=aoi %in% c("target", "distractor")) |> 
  summarize(s=sum(has_data),
            n=n()) |> 
  group_by(dataset_name) |> 
  mutate(max_n=max(n)) |> 
  ggplot(aes(x=t_norm, y=s/n, color=dataset_name))+geom_line()+facet_wrap(~dataset_name)+
  coord_cartesian(xlim=c(-4000,4050), ylim=c(0, 1))+theme(legend.position ="none")+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)

d_aoi |> group_by(dataset_name, t_norm) |> mutate(has_data=aoi %in% c("target", "distractor")) |> 
  summarize(s=sum(has_data),
            n=n()) |> 
  group_by(dataset_name) |> 
  mutate(max_n=max(n)) |> 
  ggplot(aes(x=t_norm, y=s, color=dataset_name))+geom_line()+facet_wrap(~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+theme(legend.position ="none")+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)

d_aoi |> group_by(dataset_name, t_norm, aoi) |>
  summarize(n=n()) |> 
  group_by(dataset_name) |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+
  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")


by_age <- d_aoi |> mutate(age_bin = case_when(
  age<12 ~ "<12",
  age< 18 ~ "12-18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age<48~ "36-48",
  age>=48~ ">=48")) |>
   group_by(dataset_name, t_norm, aoi, age_bin) |>
  summarize(n=n()) |> 
  group_by(dataset_name)
```


```{r}
by_age |> filter(age_bin=="<12") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```

```{r}
by_age |> filter(age_bin=="12-18") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```
```{r}
by_age |> filter(age_bin=="18-24") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```


```{r}
by_age |> filter(age_bin=="24-36") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```


```{r}
by_age |> filter(age_bin%in%c("36-48")) |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```

```{r}
by_age |> filter(age_bin%in%c(">=48")) |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```

# Summary
Exact numbers don't really matter

In general, there is benefit to going longer (ending around 3000), with 3000/4000 not mattering very much. This is particularly for ICC and TRT. For starting point, relatively later is probably better -- maybe more like 400-500? Does not make a big difference. 

Correlations to CDI are fraught -- sometimes shorter windows look better but this is driven by some datasets where there isn't (any) data for longer, also mostly holds for under 18 months. 

# <-- Older stuff begins here -->


datasets with full data at 3800
yurovsky_2017, weaver_zettersten, reflook_v4, potter_remix, pomper_yumme,
pomper_salientme, pomper_saffron, pomper_prime
garrison_bergelson
frank tablet
fmw
fernald_marchman
ferguson
bacon
adams_marchman

```{r}
acc_params <- expand_grid(
  t_start = c(0, 200, 400, 500, 600),
  t_end = c(2000, 4000),
  object = c("administration")
)
long_dataset_list = c("adams_marchman_2018", "bacon_gendercues","baumgartner_2014",
"ferguson_eyetrackingr","fernald_marchman_2012","fmw_2013","frank_tablet_2016",
"garrison_bergelson_2020","pomper_prime","pomper_saffran_2016","pomper_salientme",
"pomper_yumme","potter_remix","reflook_v4","weaver_zettersten_2024","yurovsky_2017"
)

icc_window_sim <- function(t_start = -500, t_end = 4000, object) {
  print(paste(t_start, t_end))

  df <- d_aoi |>
    filter(dataset_name%in%long_dataset_list) |> 
    filter(t_norm > t_start, t_norm < t_end) |>
    group_by(dataset_name, dataset_id, administration_id, target_label, trial_id) |>
    summarise(
      accuracy = mean(correct, na.rm = TRUE),
      prop_data = mean(!is.na(correct))
    ) |>
    filter(!is.na(accuracy)) |> 
    group_by(dataset_name, dataset_id, administration_id, target_label) |>
    mutate(repetition = row_number())

  # compute ICCs
  df |>
    group_by(dataset_name) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c())
}

tic()
accs <- acc_params |>
  # partition(cluster) |>
  mutate(icc = pmap(list(t_start, t_end, object), icc_window_sim)) |>
  # collect() |>
  unnest(col = icc)
toc()
```

```{r}
accs |> ggplot(aes(x=t_start, col=as.character(t_end), y=icc))+geom_point(position=position_dodge2(width=.5))+coord_flip()+facet_wrap(~dataset_name)+theme(legend.position = "bottom", )+labs(y="Correlation", x="Start time (ms)", color="End time")+scale_color_solarized()

accs |> ggplot(aes(x=t_start, col=as.character(t_end), y=icc))+stat_summary(fun.data="mean_cl_boot", position=position_dodge(width=50))+coord_flip()+theme(legend.position = "bottom", )+labs(y="Correlation", x="Start time (ms)", color="End time")+scale_color_solarized()

```

