---
title: "Accuracies"
author: "Veronica"
date: "27-Feb-2026"
output: 
  html_document:
    toc: true
---

One common measure from LWL times is accuracy which is measured as the proportion of the time the child is looking at the target out of the time they are looking at either the distractor or the target. 

The data-processing decision is what that window should be -- when should it start and when should it end. (Other questions about whether to baseline-correct and whether to do exclusions based on amount of data covered in later notebooks). 

```{r, echo=F, include=F}
knitr::opts_chunk$set(warning=F, message=F, echo=F)
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))

library(here)
d_aoi <- readRDS(here("cached_intermediates", "0_d_aoi.rds"))
t_increment <- 200
```


```{r}
datasets <- d_aoi |> select(trial_id, dataset_name, administration_id, subject_id) |> distinct() 

datasets |> distinct(dataset_name)

datasets |> distinct(administration_id)

datasets |> distinct(trial_id)

cdi_data <- readRDS(here("cached_intermediates", "0_cdi_subjects.rds"))

```

how much data do we have?




```{r}
#looks like all datasets have lots of trials
d_aoi |> filter(!is.na(correct)) |> group_by(dataset_name, t_norm)|> tally() |>  ggplot(aes(x=t_norm, y=n, fill=dataset_name, color=dataset_name))+geom_col()+facet_wrap(~dataset_name, scales="free_y")+theme(legend.position = "none")

```
# A digression of understanding why we get some weird ICC values

garrison bergelson (doesn't have bootstrapped CI??)
* byers-heinlein 2017 (0)
* kartushina (0)
* moore bergelson (0)
* swingley aslin 2002 (negative lower)
* borovsky 2019 (negative lower)

```{r}
# from agreement package so we can understand the innards

library(rlang)
library(assertthat)
prep_data_dim <- function(.data, object, rater, score, trial) {

  d <- list()

  df <- as_tibble(.data)
  if (rlang::quo_is_null(rlang::enquo(trial))) {
    df <- dplyr::mutate(df, Trial = "T1")
    trial <- rlang::quo(Trial)
  }
  df <- dplyr::select(df, {{object}}, {{rater}}, {{trial}}, {{score}})
  df <- tidyr::complete(df, {{object}}, {{rater}}, {{trial}})
  df <- dplyr::arrange(df, {{trial}}, {{rater}}, {{object}})
  d$objects <- unique(dplyr::pull(df, {{object}}))
  d$raters <- unique(dplyr::pull(df, {{rater}}))
  d$trials <- unique(dplyr::pull(df, {{trial}}))
  d$n_objects <- length(d$objects)
  d$n_raters <- length(d$raters)
  d$n_trials <- length(d$trials)
  scores <- dplyr::pull(df, {{score}})
  scores[is.nan(scores)] <- NA
  d$n_missing_scores <- sum(are_na(scores))
  d$min_score <- min(scores, na.rm = TRUE)
  d$max_score <- max(scores, na.rm = TRUE)
  d$ratings <- array(
    scores,
    dim = c(d$n_objects, d$n_raters, d$n_trials),
    dimnames = list(d$objects, d$raters, d$trials)
  )

  d
}

icc_counts <- function(ratings) {

  n <- list()

  # Count of objects
  n$objects <- dim(ratings)[[1]]

  # Count of raters
  n$raters <- dim(ratings)[[2]]

  # Count of trials per object-rater combination
  n$trials_or <- apply(is.finite(ratings), MARGIN = 1:2, FUN = sum)

  # Count of trials per object
  n$trials_o <- rowSums(n$trials_or)

  # Count of trials per rater
  n$trials_r <- colSums(n$trials_or)

  # Count of all trials
  n$trials <- sum(n$trials_or)

  n
}

icc_sums <- function(ratings, n = NULL) {

  if (is_null(n)) {n <- icc_counts(ratings)}

  s <- list()

  # Sum all trials per object-rater combination
  ysum_or <- apply(ratings, MARGIN = 1:2, FUN = sum, na.rm = TRUE)

  # Sum of all ratings per object
  ysum_o <- apply(ratings, MARGIN = 1, FUN = sum, na.rm = TRUE)

  # Sum of all ratings per rater
  ysum_r <- apply(ratings, MARGIN = 2, FUN = sum, na.rm = TRUE)

  # Total sum of ratings
  s$T_y <- sum(ysum_or, na.rm = TRUE)

  # Total sum of squared ratings
  s$T_ysq <- sum(ratings^2, na.rm = TRUE)

  # Sum of all object's averaged squared ratings
  s$T_objects <- sum(ysum_o^2 / n$trials_o, na.rm = TRUE)

  # Sum of all raters' average squared ratings
  s$T_raters <- sum(ysum_r^2 / n$trials_r, na.rm = TRUE)

  # Sum of all object-rater combinations' average squared ratings
  s$T_interaction <- sum(ysum_or^2 / n$trials_or, na.rm = TRUE)

  # Sum of all average ratings
  s$T_musq <- n$trials * mean(ratings, na.rm = TRUE)^2

  # Number of object-rater combinations for which one or more trials exist
  s$lambda_0 <- sum(n$trials_or > 0)

  # Expected number of trials per object
  s$k_r <- sum(n$trials_or^2 / n$trials_r)

  # Expected number of trails per rater
  s$k_o <- sum(n$trials_or^2 / n$trials_o)

  # TODO: Write informative comment
  s$kprime_o <- sum(n$trials_o^2) / n$trials
  s$kprime_r <- sum(n$trials_r^2) / n$trials
  s$kprime_or <- sum(n$trials_or^2) / n$trials
  s$Tprimesq_ysq <- s$T_y^2 / n$trials

  # TODO: Write informative comment
  s$lambda_1 <- (n$trials - s$kprime_o) / (n$trials - s$k_r)
  s$lambda_2 <- (n$trials - s$kprime_r) / (n$trials - s$k_o)

  s
}

icc_model2A <- function(ratings, n = NULL, s = NULL) {

  if (is_null(n)) {n <- icc_counts(ratings)}
  if (is_null(s)) {s <- icc_sums(ratings, n)}

  v <- list()

  v$residual <- (s$lambda_2 * (s$T_ysq - s$T_objects) + s$lambda_1 * (s$T_ysq - s$T_raters) - (s$T_ysq - s$T_musq)) /
    (s$lambda_2 * (n$trials - n$objects) + s$lambda_1 * (n$trials - n$raters) - (n$trials - 1))

  v$object <- (s$T_ysq - s$T_raters - v$residual * (n$trials - n$raters)) / (n$trials - s$k_r)

  v$rater <- (s$T_ysq - s$T_objects - v$residual * (n$trials - n$objects)) / (n$trials - s$k_o)

  v
}

nonneg <- function(x) {
  max(c(0, x))
}

# we only care about 2A consistency 
calc_inter_icc <- function(v, k) {
  inter_icc <- NA_real_
  v2 <- lapply(v, nonneg)
    inter_icc <- v2$object / (v2$object + v2$residual / k)
  inter_icc
}

calc_icc_2A_C <- function(ratings, k = 1) {

  n <- icc_counts(ratings)
  s <- icc_sums(ratings, n)
  v <- icc_model2A(ratings, n, s)
  
  View(v)
  
  v2 <- lapply(v, nonneg)

  # Create and label output vector
  out <- c(
    Object = v$object,
    Rater = NA_real_,
    Interaction = NA_real_,
    Residual = v$residual,
    Intra_ICC = NA_real_,
    Inter_ICC = calc_inter_icc(v, k)
  )

  out
}


```


```{r}
do_dim_icc <- function(.data,
                    model = c("1A", "1B", "2", "2A", "3", "3A"),
                    type = c("agreement", "consistency"),
                    unit = c("single", "average", "custom"),
                    object = Object,
                    rater = Rater,
                    score = Score,
                    customk = NULL,
                    trial = NULL,
                    bootstrap = 2000,
                    warnings = TRUE) {

  # Validate inputs
  assert_that(is.data.frame(.data) || is.matrix(.data))
  model <- match.arg(model)
  type <- match.arg(type)
  unit <- match.arg(unit)
  assert_that(bootstrap == 0 || is.count(bootstrap),
    msg = "The 'bootstrap' argument must be a non-negative integer.")
  assert_that(is.flag(warnings))
  assert_that(is.null(customk) || is.count(customk),
    msg = "The 'customk' argument must be NULL or a positive integer.")

  # Prepare .data for analysis
  d <- prep_data_dim(.data, {{object}}, {{rater}}, {{score}}, {{trial}})

  #print(d)
  
  if (unit == "single") {
    k <- 1
  } else if (unit == "average") {
    k <- d$n_raters
  } else {
    k <- customk
  }
  assert_that(is.null(k) == FALSE)

  print(k)
  
  # Prepare empty output in case of errors
  out <- new_icc(
    Object = NA_real_,
    Rater = NA_real_,
    Interaction = NA_real_,
    Residual = NA_real_,
    Intra_ICC = NA_real_,
    Inter_ICC = NA_real_,
    boot_results = list(t = matrix(NA, nrow = 1, ncol = 6), t0 = rep(NA, 6)),
    formulation = list(model = model, type = type, unit = unit, k = k),
    details = d,
    call = match.call()
  )

  # Warn about bootstrapping samples with less than 20 objects
  if (d$n_objects < 20 && bootstrap > 0 && warnings == TRUE) {
    warning("With a small number of objects, bootstrap confidence intervals may not be stable.")
  }

  # Error with impossible combinations of arguments
  if (type == "consistency" && (model == "1A" || model == "1B")) {
    stop("Consistency ICCs are not possible for models 1A and 1B.")
  }

  # Warn about there being fewer than 2 raters
  if (d$n_raters < 2) {
    if (warnings == TRUE) {
      warning("Only a single rater was observed. Returning NA.")
    }
    return(out)
  }
  #TODO: Check on intra-rater reliability with one rater - is it possible?

  if (d$n_objects < 2) {
    if (warnings == TRUE) {
      warning("Only a single object with scores was observed. Returning NA.")
    }
    return(out)
  }

  # Create function to perform bootstrapping
  boot_function <- function(codes, index, fun, k) {
    resample <- codes[index, , , drop = FALSE]
    bsr <- fun(ratings = resample, k = k)
    bsr
  }

  # Build function name for the requested ICC
  fun <- eval(
    parse(
      text = paste0("calc_icc_", model, ifelse(type == "agreement", "_A", "_C"))
    )
  )

  # Calculate the bootstrap results
  boot_results <-
    boot::boot(
      data = d$ratings,
      statistic = boot_function,
      R = bootstrap,
      fun = fun,
      k = k
    )

  # Construct icc class output object
  out <- new_icc(
    Object = boot_results$t0[[1]],
    Rater = boot_results$t0[[2]],
    Interaction = boot_results$t0[[3]],
    Residual = boot_results$t0[[4]],
    Intra_ICC = boot_results$t0[[5]],
    Inter_ICC = boot_results$t0[[6]],
    boot_results = boot_results,
    formulation = list(model = model, type = type, unit = unit, k = k),
    details = d,
    call = match.call()
  )

  out
}

# Functions to calculate ICC components -----------------------------------

icc_counts <- function(ratings) {

  n <- list()

  # Count of objects
  n$objects <- dim(ratings)[[1]]

  # Count of raters
  n$raters <- dim(ratings)[[2]]

  # Count of trials per object-rater combination
  n$trials_or <- apply(is.finite(ratings), MARGIN = 1:2, FUN = sum)

  # Count of trials per object
  n$trials_o <- rowSums(n$trials_or)

  # Count of trials per rater
  n$trials_r <- colSums(n$trials_or)

  # Count of all trials
  n$trials <- sum(n$trials_or)

  n
}

icc_sums <- function(ratings, n = NULL) {

  if (is_null(n)) {n <- icc_counts(ratings)}

  s <- list()

  # Sum all trials per object-rater combination
  ysum_or <- apply(ratings, MARGIN = 1:2, FUN = sum, na.rm = TRUE)

  # Sum of all ratings per object
  ysum_o <- apply(ratings, MARGIN = 1, FUN = sum, na.rm = TRUE)

  # Sum of all ratings per rater
  ysum_r <- apply(ratings, MARGIN = 2, FUN = sum, na.rm = TRUE)

  # Total sum of ratings
  s$T_y <- sum(ysum_or, na.rm = TRUE)

  # Total sum of squared ratings
  s$T_ysq <- sum(ratings^2, na.rm = TRUE)

  # Sum of all object's averaged squared ratings
  s$T_objects <- sum(ysum_o^2 / n$trials_o, na.rm = TRUE)

  # Sum of all raters' average squared ratings
  s$T_raters <- sum(ysum_r^2 / n$trials_r, na.rm = TRUE)

  # Sum of all object-rater combinations' average squared ratings
  s$T_interaction <- sum(ysum_or^2 / n$trials_or, na.rm = TRUE)

  # Sum of all average ratings
  s$T_musq <- n$trials * mean(ratings, na.rm = TRUE)^2

  # Number of object-rater combinations for which one or more trials exist
  s$lambda_0 <- sum(n$trials_or > 0)

  # Expected number of trials per object
  s$k_r <- sum(n$trials_or^2 / n$trials_r)

  # Expected number of trails per rater
  s$k_o <- sum(n$trials_or^2 / n$trials_o)

  # TODO: Write informative comment
  s$kprime_o <- sum(n$trials_o^2) / n$trials
  s$kprime_r <- sum(n$trials_r^2) / n$trials
  s$kprime_or <- sum(n$trials_or^2) / n$trials
  s$Tprimesq_ysq <- s$T_y^2 / n$trials

  # TODO: Write informative comment
  s$lambda_1 <- (n$trials - s$kprime_o) / (n$trials - s$k_r)
  s$lambda_2 <- (n$trials - s$kprime_r) / (n$trials - s$k_o)

  s
}

icc_model2A <- function(ratings, n = NULL, s = NULL) {

  if (is_null(n)) {n <- icc_counts(ratings)}
  if (is_null(s)) {s <- icc_sums(ratings, n)}

  v <- list()

  v$residual <- (s$lambda_2 * (s$T_ysq - s$T_objects) + s$lambda_1 * (s$T_ysq - s$T_raters) - (s$T_ysq - s$T_musq)) /
    (s$lambda_2 * (n$trials - n$objects) + s$lambda_1 * (n$trials - n$raters) - (n$trials - 1))

  v$object <- (s$T_ysq - s$T_raters - v$residual * (n$trials - n$raters)) / (n$trials - s$k_r)

  v$rater <- (s$T_ysq - s$T_objects - v$residual * (n$trials - n$objects)) / (n$trials - s$k_o)

  print(v)
  v
}


# Function to calculate ICCs ----------------------------------------------

calc_inter_icc <- function(v, k, model, type) {
  inter_icc <- NA_real_
  v2 <- lapply(v, nonneg)
  if (model == "1A") {
    inter_icc <- v2$object / (v2$object + v2$residual / k)
  } else if (model == "2" && type == "agreement") {
    inter_icc <- v2$object /
      (v2$object + (v2$rater + v2$interaction + v2$residual) / k)
  } else if (model == "2" && type == "consistency") {
    inter_icc <- v2$object /
      (v2$object + (v2$interaction + v2$residual) / k)
  } else if (model == "2A" && type == "agreement") {
    inter_icc <- v2$object / (v2$object + (v2$rater + v2$residual) / k)
  } else if (model == "2A" && type == "consistency") {
    inter_icc <- v2$object / (v2$object + v2$residual / k)
  }
  inter_icc
}


# Consistency ICC under Model 2A
# Model 2A applies when both raters and objects are random, excludes interaction
calc_icc_2A_C <- function(ratings, k = 1) {

  n <- icc_counts(ratings)
  s <- icc_sums(ratings, n)
  v <- icc_model2A(ratings, n, s)

  print(v)
  v2 <- lapply(v, nonneg)

  # Create and label output vector
  out <- c(
    Object = v$object,
    Rater = NA_real_,
    Interaction = NA_real_,
    Residual = v$residual,
    Intra_ICC = NA_real_,
    Inter_ICC = calc_inter_icc(v, k, "2A", "consistency")
  )

  #print(out)
  out
}

new_icc <- function(Object = double(),
                    Rater = double(),
                    Interaction = double(),
                    Residual = double(),
                    Intra_ICC = double(),
                    Inter_ICC = double(),
                    boot_results = list(),
                    formulation = list(),
                    details = list(),
                    call = rlang::quo(),
                    ...) {

  new_s3_scalar(
    Object = Object,
    Rater = Rater,
    Interaction = Interaction,
    Residual = Residual,
    Intra_ICC = Intra_ICC,
    Inter_ICC = Inter_ICC,
    boot_results = boot_results,
    formulation = formulation,
    details = details,
    call = call,
    ...,
    class = "agreement_icc"
  )

}

new_s3_lst <- function(x, ..., class) {
  stopifnot(is.list(x))
  stopifnot(is.character(class))
  structure(x, ..., class = class)
}

# Create a new S3 class from a scalar
new_s3_scalar <- function(..., class) {
  new_s3_lst(list(...), class = class)
}


```


```{r}
df <- d_aoi |>
    filter(t_norm > 200, t_norm < 2000) |>
    group_by(dataset_name, dataset_id, administration_id, target_label, trial_id) |>
    summarise(
      accuracy = mean(correct, na.rm = TRUE),
      prop_data = mean(!is.na(correct))
    ) |>
    filter(!is.na(accuracy)) |> 
    group_by(dataset_name, dataset_id, administration_id, target_label) |>
    mutate(repetition = row_number())
```


```{r}
# compute ICCs
 gb <-  df |> filter(dataset_name=="garrison_bergelson_2020") |> filter(!is.na(accuracy))|> prep_data_dim( administration_id, target_label, accuracy, repetition)

#print(gb)

calc_icc_2A_C(gb$ratings, gb$n_raters)
 
 df |> filter(dataset_name=="garrison_bergelson_2020") |> filter(!is.na(accuracy)) |>  do_dim_icc(
    model = "2A",
    type = "consistency",
    unit = "average",
    object = administration_id,
    rater = target_label,
    trial = repetition,
    score = accuracy,
    bootstrap = 10
  )
```

```{r}
# compute ICCs
 wz <-  df |> filter(dataset_name=="weaver_zettersten_2024") |> filter(!is.na(accuracy))|> prep_data_dim( administration_id, target_label, accuracy, repetition)

calc_icc_2A_C(wz$ratings)


 df |>filter(dataset_name=="weaver_zettersten_2024") |> 
    group_by(dataset_name) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy")))) |>
    select(-data) |>
    unnest(cols = c())
```

```{r}
# compute ICCs
 gb <-  df |> filter(dataset_name=="garrison_bergelson_2020") |> filter(!is.na(accuracy))|> prep_data_dim( administration_id, target_label, accuracy, repetition)

calc_icc_2A_C(gb$ratings)


 df |>filter(dataset_name=="garrison_bergelson_2020") |> 
    group_by(dataset_name) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy")))) |>
    select(-data) |>
    unnest(cols = c())

```


# Data prep

## No boot ICC
```{r, eval=F}
icc_window_sim <- function(t_start = -500, t_end = 4000, object) {
  print(paste(t_start, t_end))

  df <- d_aoi |>
    filter(t_norm > t_start, t_norm < t_end) |>
    group_by(dataset_name, dataset_id, administration_id, target_label, trial_id) |>
    summarise(
      accuracy = mean(correct, na.rm = TRUE),
      prop_data = mean(!is.na(correct))
    ) |>
    filter(!is.na(accuracy)) |> 
    group_by(dataset_name, dataset_id, administration_id, target_label) |>
    mutate(repetition = row_number())

  # compute ICCs
  df |>
    group_by(dataset_name) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c())
}

acc_params <- expand_grid(
  t_start = seq(-500, 1500, 100),
  t_end = seq(2000, 4000, 100),
  object = c("administration")
)


tic()
accs <- acc_params |>
  mutate(icc = pmap(list(t_start, t_end, object), icc_window_sim)) |>
  unnest(col = icc)
toc()

saveRDS(accs, here("cached_intermediates", "1_acc_icc_noboot.rds"))
```

and by age

```{r, eval=F}
#admins/dataset in each agebin
d_aoi |> filter(!is.na(correct)) |> make_age_bins()|> ggplot(aes(x=age_bin, fill=dataset_name))+geom_histogram(stat="count")


d_aoi |> filter(!is.na(correct)) |> distinct(administration_id, age, dataset_name) |>    mutate(age_bin = case_when(
  age< 18 ~ "<18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age>=36~ ">=36")) |>
group_by(dataset_name, age_bin) |> tally() |> arrange(n)

# apply a cutoff of at least 5 kids going into an age-bin x paper

age_bin_cutoff <-d_aoi |> filter(!is.na(correct)) |> distinct(administration_id, age, dataset_name) |>    mutate(age_bin = case_when(
  age< 18 ~ "<18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age>=36~ ">=36")) |>
group_by(dataset_name, age_bin) |> mutate(count=n()) |> filter(count>=5) |> ungroup()

```

```{r, eval=F}
icc_window_sim_age <- function(t_start = -1000, t_end = 4000, object) {
  df <- d_aoi |> inner_join(age_bin_cutoff) |> 
    filter(t_norm > t_start, t_norm < t_end) |>
    group_by(
      dataset_name, dataset_id, age_bin, administration_id,
      target_label, trial_id
    ) |>
    summarise(
      accuracy = mean(correct, na.rm = TRUE),
      prop_data = mean(!is.na(correct))
    ) |> 
    filter(!is.na(accuracy)) |> 
    group_by(dataset_name, age_bin, dataset_id, administration_id, target_label) |>
    mutate(repetition = row_number())

  # compute ICCs
  df |>
    group_by(dataset_name, age_bin) |>
    nest() |>
    mutate(icc = unlist(map(data, ~ get_icc(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c())
}

t_increment <- 200

acc_params <- expand_grid(
  t_start = seq(-1000, 1500, t_increment),
  t_end = seq(2000, 4000, t_increment),
  object = c("administration")
)


accs_byage <- acc_params |>
  mutate(icc = pmap(list(t_start, t_end, object), icc_window_sim_age)) |>
  unnest(col = icc)

saveRDS(accs_byage, here("cached_intermediates", "1_acc_icc_noboot_byage.rds"))

```

## Scripts

```{r, eval=F}
source(here("scripts/1_acc_icc_boot.R"))
source(here("scripts/1_acc_cdi_boot.R"))
source(here("scripts/1_acc_test_retest_boot.R"))

```

# Visualizations

## Heatmap noboot ICC

```{r}
icc_noboot <- readRDS(here("cached_intermediates", "1_acc_icc_noboot.rds"))

icc_noboot_summary <- icc_noboot |>
  group_by(t_start, t_end) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  mutate(window_size = t_end - t_start)


ggplot(icc_noboot_summary, aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c(-1000, -500, 0, 500, 1000, 1500)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

ggplot(
  icc_noboot_summary,
  aes(color = mean_icc)
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_segment(aes(x = t_start, xend = t_end, y = mean_icc, yend = mean_icc)) +
  geom_segment(aes(x = t_start, xend = t_start, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  geom_segment(aes(x = t_end, xend = t_end, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  scale_color_viridis(name = "Mean ICC", direction = -1) +
  theme(legend.position = "none") +
  ylab("Mean ICC") +
  xlab("Analysis Window (in ms)")
```

For datasets with data up to at least 3800
```{r}
long_datasets <- d_aoi |> group_by(dataset_name) |> summarize(min_t_norm=min(t_norm), max_t_norm=max(t_norm), count_0=sum(t_norm==0), count_2000=sum(t_norm==2000), count_3800=sum(t_norm==3800)) |> filter(min_t_norm<=0, max_t_norm>=2000) |> filter(count_0/count_2000>.8) |> filter(count_3800/count_2000>.8)

long_datasets
```


```{r}
icc_noboot |> semi_join(long_datasets) |> group_by(t_start, t_end) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  filter(t_start>=0) |> 
  mutate(window_size = t_end - t_start) |> 
  ggplot(aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c( 0, 500, 1000, 1500)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

icc_noboot |> semi_join(long_datasets) |> group_by(t_start, t_end, dataset_name) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  group_by(dataset_name) |> 
  mutate(relative=mean_icc/max(mean_icc),
         relative2=mean_icc-max(mean_icc)) |> 
  filter(t_start>=0, t_start<800) |> 
  mutate(window_size = t_end - t_start) |> 
  ggplot(aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c( 0, 500, 1000, 1500)) +
  facet_wrap(~dataset_name)+
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

```



```{r}
icc_noboot_byage <- readRDS(here("cached_intermediates", "1_acc_icc_noboot_byage.rds"))

icc_noboot_byage_summary <- icc_noboot_byage |>
  group_by(t_start, t_end, age_bin) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  mutate(window_size = t_end - t_start)


ggplot(icc_noboot_byage_summary, aes(x = t_start, y = t_end, fill = mean_icc)) +
  facet_wrap(~age_bin)+
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "inferno") +
  scale_x_continuous(breaks = c(-1000, -500, 0, 500, 1000, 1500)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")

ggplot(
  icc_noboot_byage_summary,
  aes(color = mean_icc)
) +
  facet_wrap(~age_bin)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_segment(aes(x = t_start, xend = t_end, y = mean_icc, yend = mean_icc)) +
  geom_segment(aes(x = t_start, xend = t_start, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  geom_segment(aes(x = t_end, xend = t_end, y = mean_icc - 0.005, yend = mean_icc + 0.005)) +
  scale_color_viridis(name = "Mean ICC", direction = -1) +
  theme(legend.position = "none") +
  ylab("Mean ICC") +
  xlab("Analysis Window (in ms)")
```

## Bootstrapped ICC


```{r}
acc_boot <- readRDS(here("cached_intermediates/1_acc_icc_boot.rds"))

acc_boot_summary <- acc_boot |> do_meta(c("t_start", "t_end"))

acc_boot_summary_long <- acc_boot |> semi_join(long_datasets) |> do_meta(c("t_start", "t_end"))
```

Looking overall

```{r}
acc_boot_summary |> ggplot(aes(x = t_start, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 25))

acc_boot_summary_long |> ggplot(aes(x = t_start, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 25))
```
### by age

```{r}
acc_boot_age <- readRDS(here("cached_intermediates/1_acc_icc_boot_byage.rds"))
acc_boot_age_summary <- acc_boot_age |> do_meta(c("t_start", "t_end", "age_bin"))
```


```{r}
acc_boot_age_summary |> ggplot(aes(x = t_start, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.character(t_end))) +
  geom_pointrange(position = position_dodge(width = 50))+facet_wrap(~age_bin, scales="free_y")+theme(legend.position = "bottom")

```


## CDI corr

Reliability measures like ICC tell us how consistently we're measuring *something*, but they don't tell us what the *something* we're measuring is. For that, we want a check on validity, so we look at the correlation between accuracy (measured on different windows) with each of CDI production measures, CDI comprehension measures, and age. 



```{r}
accs_cdi <- readRDS(here("cached_intermediates", "1_acc_cdi_boot.rds"))

accs_cdi_summ <- accs_cdi |> do_cdi_meta(c("t_start", "t_end"))

accs_cdi_summ_long <- accs_cdi |> semi_join(long_datasets) |> do_cdi_meta(c("t_start", "t_end"))
```




Correlation with production

```{r}
accs_cdi_summ |> ggplot(aes(x = t_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi_summ_long |> ggplot(aes(x = t_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

```
All of these show the expected positive correlation between CDI production and accuracy. Kids who say more words are more accurate.
Correlation with comprehension

```{r}
accs_cdi_summ |> ggplot(aes(x = t_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi_summ_long |> ggplot(aes(x = t_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

```
Looking at comprehension, there aren't big differences, but we see higher correlations with shorter windows (peaking starting at 400ms). For long windows, peak seems to be for really long like 0-4000ms. 
Again, correlation is positive, as expected!


Correlation with age

Correlating with age isn't a validity check per se, so much as a "if it doesn't correlate with age, we worry" check. 

```{r}
accs_cdi_summ |> ggplot(aes(x = t_start, y = age_estimate, ymin=age_ci.lb, ymax=age_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

accs_cdi_summ_long |> ggplot(aes(x = t_start, y = age_estimate, ymin=age_ci.lb, ymax=age_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()

```
Overall, there is a positive correlation with age that is not very effected by windowing choices. 

### by age 


```{r}
accs_cdi_byage <- readRDS(here("cached_intermediates", "1_acc_cdi_boot_byage.rds"))

accs_cdi_summ_age <- accs_cdi_byage |> do_cdi_meta(c("t_start", "t_end", "age_bin"))
```


Correlation with production

```{r}
accs_cdi_summ_age |> filter(!is.na(prod_estimate)) |>  ggplot(aes(x = t_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~age_bin)

```
All of these show the expected positive correlation between CDI production and accuracy. Kids who say more words are more accurate.
Correlation with comprehension

```{r}
accs_cdi_summ_age |> filter(!is.na(comp_estimate)) |>  ggplot(aes(x = t_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~age_bin)

```
Looking at comprehension, there aren't big differences, but we see higher correlations with shorter windows (peaking starting at 400ms). For long windows, peak seems to be for really long like 0-4000ms. 
Again, correlation is positive, as expected!


Correlation with age

Correlating with age isn't a validity check per se, so much as a "if it doesn't correlate with age, we worry" check. 

```{r}
accs_cdi_summ_age |> ggplot(aes(x = t_start, y = age_estimate, ymin=age_ci.lb, ymax=age_ci.ub, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~age_bin)

```
Overall, there is a positive correlation with age that is not very effected by windowing choices. 

```{r}
accs_cdi_byage |> filter(age_bin=="<18") |>  filter(!is.na(age_est))|> ggplot(aes(x = t_start, y = age_est, ymin=age_lower, ymax=age_upper, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~dataset_name)

accs_cdi_byage |> filter(age_bin=="<18") |>  filter(!is.na(prod_est))|> ggplot(aes(x = t_start, y = prod_est, ymin=prod_lower, ymax=prod_upper, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~dataset_name)

accs_cdi_byage |> filter(age_bin=="<18") |>  filter(!is.na(comp_est))|> ggplot(aes(x = t_start, y = comp_est, ymin=comp_lower, ymax=comp_upper, color=as.character(t_end))) +geom_pointrange(position=position_dodge(width=50))+coord_flip()+facet_wrap(~dataset_name)
```


## Test retest


```{r}
accs_kid_test_retest <- readRDS(here("cached_intermediates", "1_acc_test_retest_boot.rds"))

accs_kid_test_retest_summ <-  accs_kid_test_retest |> do_meta(c("t_start", "t_end"))
```


```{r}
accs_kid_test_retest |> ggplot(aes(x=t_start, y=est, ymin=lower, ymax=upper, color=as.character(t_end)))+geom_pointrange(position = position_dodge(width=50))+facet_wrap(~dataset_name)+geom_hline(yintercept=0)
```


```{r}
accs_kid_test_retest_summ |> ggplot(aes(x=t_start, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(t_end)))+geom_pointrange(position = position_dodge(width=50))+geom_hline(yintercept=0)

```




# how much t/d looking on longer places (and in what datasets)

```{r}
d_aoi |> group_by(dataset_name, t_norm) |> mutate(has_data=aoi %in% c("target", "distractor")) |> 
  summarize(s=sum(has_data),
            n=n()) |> 
  ggplot(aes(x=t_norm, y=n))+geom_col(fill="blue")+facet_wrap(~dataset_name, scales="free_y") +
  coord_cartesian(xlim=c(0,4050))+geom_vline(xintercept=3800)

d_aoi |> group_by(dataset_name, t_norm) |> mutate(has_data=aoi %in% c("target", "distractor")) |> 
  summarize(s=sum(has_data),
            n=n()) |> 
  group_by(dataset_name) |> 
  mutate(max_n=max(n)) |> 
  ggplot(aes(x=t_norm, y=s/n, color=dataset_name))+geom_line()+facet_wrap(~dataset_name)+
  coord_cartesian(xlim=c(-4000,4050), ylim=c(0, 1))+theme(legend.position ="none")+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)

d_aoi |> group_by(dataset_name, t_norm) |> mutate(has_data=aoi %in% c("target", "distractor")) |> 
  summarize(s=sum(has_data),
            n=n()) |> 
  group_by(dataset_name) |> 
  mutate(max_n=max(n)) |> 
  ggplot(aes(x=t_norm, y=s, color=dataset_name))+geom_line()+facet_wrap(~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+theme(legend.position ="none")+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)

d_aoi |> group_by(dataset_name, t_norm, aoi) |>
  summarize(n=n()) |> 
  group_by(dataset_name) |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+
  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")


by_age <- d_aoi |> mutate(age_bin = case_when(
  age<12 ~ "<12",
  age< 18 ~ "12-18",
  age < 24~ "18-24",
  age< 36~ "24-36",
  age<48~ "36-48",
  age>=48~ ">=48")) |>
   group_by(dataset_name, t_norm, aoi, age_bin) |>
  summarize(n=n()) |> 
  group_by(dataset_name)
```


```{r}
by_age |> filter(age_bin=="<12") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```

```{r}
by_age |> filter(age_bin=="12-18") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```
```{r}
by_age |> filter(age_bin=="18-24") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```


```{r}
by_age |> filter(age_bin=="24-36") |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```


```{r}
by_age |> filter(age_bin%in%c("36-48")) |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```

```{r}
by_age |> filter(age_bin%in%c(">=48")) |> 
  ggplot(aes(x=t_norm, y=n, fill=aoi, color=aoi))+geom_col(position="stack")+facet_wrap(age_bin~dataset_name, scales="free_y")+
  coord_cartesian(xlim=c(-4000,4050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=2000)+geom_vline(xintercept=3000)+geom_vline(xintercept=4000)+  scale_fill_manual(aesthetics=c("fill", "color"), values=c("target"="darkgreen", "distractor"="red", "missing"="grey", "other"="grey"))+theme(legend.position="bottom")
```

# Summary
Exact numbers don't really matter

In general, there is benefit to going longer (ending around 3000), with 3000/4000 not mattering very much. This is particularly for ICC and TRT. For starting point, relatively later is probably better -- maybe more like 400-500? Does not make a big difference. 

Correlations to CDI are fraught -- sometimes shorter windows look better but this is driven by some datasets where there isn't (any) data for longer, also mostly holds for under 18 months. 
