---
title: "Baseline correction"
author: "Mike Frank"
date: "2022-12-15"
output: html_document
---



```{r}
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))
d_aoi <- readRDS(here("cached_intermediates", "0_d_aoi.rds"))
```


# Baseline-corrected accuracy general approach

Accuracy measures are just about where a child looks after they have heard the stimulus, but this is not necessarily the best measure of children's *response* to the stimulus, as children's looking patterns could also be driven by item-level effects. For instance, children may look more at the more salient, more animate, or more recently referred to object. 

Researchers have tried a few approaches for "correcting" for these baseline preferences. Options include

* a baseline-corrected accuracy where the fraction of looking at target prior to stimulus response is subtracted from the post-stimulus accuracy (thus adjusting for baseline looking preference)

* using paired trials where each was the target to see if during the post-stimulus period an item is looked at more as the target

* (other approaches)

Here we'll just look at whether using the difference between post- and pre- accuracy affects reliability and/or validity compared to plain "post-stimulus" accuracy measures. 

Throughout here, we treat the "normal" window as 400 - 3000ms (which is within the range of reasonable according to the accuracy analysis), and vary the size of the pre-window. 

# What datasets have pre information?

Different datasets have aois for different time periods. 

```{r}
ggplot(d_aoi, aes(x = t_norm)) +
  geom_histogram() +
  facet_wrap(~dataset_name, scales = "free_y") +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 400)

baseline_lengths <- d_aoi |>
    group_by(dataset_name) |>
    summarise(t_min = min(t_norm), .groups = "drop")
```

# Data prep
See scripts
# Viz
## ICC

```{r}
bc_boot <- readRDS(here("cached_intermediates", "2_bc_icc_boot.rds")) 
no_bc_boot <- readRDS(here("cached_intermediates", "1_acc_icc_boot.rds")) |> filter(t_start == 400)
  
bc_icc <- bc_boot |>
  bind_rows(no_bc_boot) |> semi_join(baseline_lengths |> filter(t_min<0)) |> 
  mutate(b_start = ifelse(is.na(b_start), "none", as.character(b_start))) |> do_meta(c("b_start", "b_end", "t_start", "t_end"))
```

```{r}
bc_icc |> ggplot(aes(x = b_start, color = as.character(b_end), y = estimate, ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position = position_dodge(width = .25))+facet_wrap(t_start~t_end)
```

```{r}
bc_icc_early_summ <- bc_boot |>
  bind_rows(no_bc_boot) |> semi_join(baseline_lengths |> filter(t_min < -3000)) |> 
  mutate(b_start = ifelse(is.na(b_start), "none", as.character(b_start))) |> do_meta(c("b_start", "b_end", "t_start", "t_end"))

bc_icc_early_summ |> ggplot(aes(x = b_start, color = as.character(b_end), y = estimate, ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position = position_dodge(width = .25))+ facet_wrap(t_start~t_end)
```

### by age

```{r}
bc_boot_age <- readRDS(here("cached_intermediates", "2_bc_icc_boot_byage.rds"))
no_bc_boot_age <- readRDS(here("cached_intermediates", "1_acc_icc_boot_byage.rds")) |> filter(t_start == 400)

bc_boot_age_summ <- bc_boot_age |>
  bind_rows(no_bc_boot_age) |>   inner_join(baseline_lengths |> filter(t_min < 0)) |>
  mutate(b_start = ifelse(is.na(b_start), "none", as.character(b_start))) |> do_meta(c("age_bin", "t_start", "t_end", "b_start", "b_end")) |> filter(t_end==3000)
```

```{r}

bc_boot_age_summ |> ggplot(aes(x = b_start, color = as.character(b_end), y = estimate, ymin = ci.lb, ymax = ci.ub)) + facet_wrap(~age_bin)+
  geom_pointrange(position = position_dodge(width = .25))
```
baseline correction is more of a mistake for older children (or older children tend to go with datasets with less baseline information)

## CDI



```{r}
no_bc_accs_kid_cdi <- readRDS(here("cached_intermediates", "1_acc_cdi_boot.rds")) |> filter(t_start==400)

bc_accs_kid_cdi <- readRDS(here("cached_intermediates", "2_bc_cdi_boot.rds")) |>bind_rows(no_bc_accs_kid_cdi) |> 
  mutate(b_start=ifelse(is.na(b_start), "none", as.character(b_start))) |> semi_join(baseline_lengths)

bc_accs_kid_cdi_summ <-  bc_accs_kid_cdi |>do_cdi_meta(c("t_start", "t_end", "b_start", "b_end"))
  
  bc_accs_kid_cdi_summ_early <-  bc_accs_kid_cdi |> semi_join(baseline_lengths |> filter(t_min < -3000)) |> 
    do_cdi_meta(c("t_start", "t_end", "b_start", "b_end"))

```

First we can look at the correlation with production. 

For all datasets
```{r}
bc_accs_kid_cdi_summ |> ggplot(aes(x = b_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(b_end))) +geom_pointrange(position=position_dodge(width=.5))+coord_flip()+facet_wrap(~t_end)
```



For only the "early" datasets (with data from 3 seconds before onset)
```{r}
bc_accs_kid_cdi_summ_early |> ggplot(aes(x = b_start, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(b_end))) +geom_pointrange(position=position_dodge(width=.5))+coord_flip()+facet_wrap(~t_end)
```
well, no benefit on the production data, and some weak signs of worseness, even when there is a lot of baseline. 

what about with comprehension?

across all datasets

```{r}
bc_accs_kid_cdi_summ |> ggplot(aes(x = b_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(b_end))) +geom_pointrange(position=position_dodge(width=.5))+coord_flip()+facet_wrap(~t_end)
```

for the early datasets

```{r}
bc_accs_kid_cdi_summ_early |> ggplot(aes(x = b_start, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(b_end))) +geom_pointrange(position=position_dodge(width=.5))+coord_flip()+facet_wrap(~t_end)
```
again, no evidence of benefit to baseline correcting

## Test-retest


```{r}
no_bc_accs_kid_test_retest <- readRDS(here("cached_intermediates", "1_acc_test_retest_boot.rds")) |> filter(t_start==400)

bc_accs_kid_test_retest <- readRDS(here("cached_intermediates", "2_bc_test_retest_boot.rds")) |> bind_rows(no_bc_accs_kid_test_retest) |> 
  mutate(b_start=ifelse(is.na(b_start), "none", as.character(b_start))) |> semi_join(baseline_lengths) |> filter(t_end==3000)

bc_accs_kid_test_retest_summ <- bc_accs_kid_test_retest |>  do_meta(c("t_start", "t_end", "b_start", "b_end"))

```

test-retest for each of the datasets with test-retest data 
```{r}
bc_accs_kid_test_retest |> ggplot(aes(x=b_start, y=est, ymin=lower, ymax=upper, color=as.character(b_end)))+geom_pointrange(position = position_dodge(width=.5))+facet_wrap(~dataset_name)
```
test-retest is somewhat better for long baselines for potter_remix (which does have a long baseline window); no or anti- benefit in other datasets. 

```{r}
bc_accs_kid_test_retest_summ |> ggplot(aes(x=b_start, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(b_end)))+geom_pointrange(position = position_dodge(width=.5))
```

# Summary

Tl:dr; don't baseline correct. 

If you insist on baseline correcting, you want to use a really long window (2 seconds+), and it probably still won't help, but it probably won't do much harm. There might be trade-offs between reliability and validity, we only have one dataset with both repeated measurements and a long pre-window (and it's not that big a dataset). 

There's still the separate question of how to incorporate children's looking biases into regression models to better account for item variability. (either just through mixed effects, or through mixed effects + covariate?)

