---
title: "RT Computation"
author: "Mike Frank"
date: "2022-12-15"
output: 
  html_document:
    toc: true
---

# RT options

In addition to accuracy, LWL time course data can also be turned into reaction times (RT) which seem to represent a different construct. 

Generally RT are only measured when a child shifts from the distractor to the target in response to the auditory stimulus. 

There are different options for how exactly to calculate this:

* what time point to use: one can either do "landing based rt" where the rt is to the first time the child looks at the target, or "launch based rt" when the child leaves the distractor. Launch based usually measures to the first time the child leaves the distractor.

* one could exclude cases where children take a long time between when their eyes leave the distractor (for the first or last time) and when the land on the target 

* as always, one can analyse RT either in ms or in log(ms) 

since it takes time for children to process the stimulus, the earliest stimulus-driven shift is not happening at t0 but some few hundred milliseconds later -- leading to some choices about what criteria to use to make sure that the child is on the distractor during the time when they are processing the stiumulus. We refer to this period as the "window". 
typically, children are required to be one the distractor the entire time between t_0 and the window end. however, depending on the state of missing data or imputation (and blinks and handling of tracker loss), it's possible this is too strict. 

here, we always require that children not look at the target during the window, and then consider the effects of 
* requiring children to be on the distractor at time_0
* requiring children to be on the distractor at the end of the window
* requiring children to be on the distractor a given fraction of the time between t_0 and t_end
* using different window lengths 

```{r, echo=F, include=F}
knitr::opts_chunk$set(warning = F, message = F, echo = F)
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))
d_aoi <- readRDS(here("cached_intermediates", "0_d_aoi.rds"))

```

(no need to run)
```{r, eval=F}

source(here("helper/rt_helper.R"))
source(here("scripts/4_rts.R"))
```

not all datasets are appropriate for RT analyses -- in particular

```{r}
d_rt <- readRDS(here("cached_intermediates", "3_rts.rds")) |> filter(window == 0, time_0 == T)
```

```{r}
d_rt |>
  group_by(dataset_name, shift_type) |>
  tally() |>
  group_by(dataset_name) |>
  mutate(n = n / sum(n)) |>
  pivot_wider(names_from = shift_type, values_from = n)
```

```{r}
d_aoi |>
  filter(!is.na(correct)) |>
  group_by(dataset_name, t_norm) |>
  tally() |>
  ggplot(aes(x = t_norm, y = n, fill = dataset_name, color = dataset_name)) +
  geom_col() +
  coord_cartesian(xlim=c(-100, 1050))+
  geom_vline(xintercept=0)+geom_vline(xintercept=1000)+
  facet_wrap(~dataset_name, scales = "free_y") +
  theme(legend.position = "none")
```
We need there to be data at t=0 to do RT, so we exclude the borovsky dataset. 

```{r, eval=F}
readRDS(here("cached_intermediates", "3_rts.rds")) |> filter(dataset_name!="borovsky_2019") |> left_join(d_aoi |> distinct(administration_id, age)) |> saveRDS(here("cached_intermediates", "3_rts.rds"))
```

# Viz

# ICC
```{r}
rt_icc <- readRDS(here("cached_intermediates/3_rt_icc_boot.rds"))

rt_icc_meta <- rt_icc |> do_meta(c("window", "time_0", "time_end", "during", "frac", "measure"))
```
```{r}

#normie stuff
rt_icc_meta |> regroup_rt() |> 
  ggplot(aes(y = estimate, color = window, group=window, x = str_c(logged, " ", type), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~trimming)+
  geom_hline(yintercept = .7) +
  scale_color_viridis(discrete = F)
```
getting best out of log land untrimmed (at some value)

```{r}
#normie stuff
rt_icc_meta |> regroup_rt() |> 
  filter(logged=="log", trimming=="untrimmed", type=="land") |> filter(window>300, window<700) |> 
  ggplot(aes(y = estimate, color = as.character(window), group=as.character(window), x = str_c(logged, " ", type), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~trimming)+
  geom_hline(yintercept = .7) +
  scale_color_viridis(discrete = T)
```


```{r}
#normie stuff
rt_icc_meta |> regroup_rt() |> filter(window>300, window<700) |> 
  ggplot(aes(y = estimate, color = as.character(window), group=as.character(window), x = str_c(logged, " ", type), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~trimming)+
  geom_hline(yintercept = .7) +
  scale_color_viridis(discrete = T)
```
375-400 is the best? 


you do almost as well even if you don't pay attention to where exactly the child is looking in between 0 and when you start counting as long as it isn't the target. 

## by age
```{r}
rt_icc_age <- readRDS(here("cached_intermediates/3_rt_icc_boot_byage.rds"))

rt_icc_age_meta <- rt_icc_age |> do_meta(c("window", "time_0", "time_end", "during", "frac", "measure", "age_bin"))
```

getting best out of log land untrimmed (at some value)

```{r}
#normie stuff
rt_icc_age_meta |> regroup_rt() |> 
  filter(logged=="log", trimming=="untrimmed", type=="land") |> filter(window>300, window<700) |> 
  ggplot(aes(y = estimate, color = as.character(window), group=as.character(window), x = str_c(logged, " ", type), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~age_bin)+
  geom_hline(yintercept = .7) +
  scale_color_viridis(discrete = T)
```
depends a little on age, but around 400 is reasonable (18-24 might want 500 instead)

```{r}
#normie stuff
rt_icc_age_meta |> regroup_rt()|> filter(window>300, window<700) |> 
  ggplot(aes(y = estimate, color = as.character(window), group=as.character(window), x = str_c(logged, " ", type), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_grid(age_bin~trimming)+
  geom_hline(yintercept = .7) +
  scale_color_viridis(discrete = T)
```
around 400 seems solid across age groups 

# CDI

```{r}
rt_cdi <- readRDS(here("cached_intermediates/3_rt_cdi_boot.rds")) |> regroup_rt()
rt_cdi_meta <- rt_cdi |> do_cdi_meta(c("window", "time_0", "time_end", "during", "frac", "logged", "type", "trimming"))
```

## comp
```{r}
rt_cdi_meta |> filter(window!=1000) |> ggplot(aes(x = type, y = comp_estimate, ymin = comp_ci.lb, ymax = comp_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(logged~trimming)+
  scale_color_viridis(discrete=T)

rt_cdi_meta |> filter(window>300, window<600) |> ggplot(aes(x = type, y = comp_estimate, ymin = comp_ci.lb, ymax = comp_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(logged~trimming)+
  geom_hline(yintercept=-.25)+
  scale_color_viridis(discrete=T)
```
log is better; best is first launch 425 trim first, but land/log/untrimmed 425 is also pretty good 

## prod
```{r}
rt_cdi_meta |> filter(window!=1000) |> ggplot(aes(x = type, y = prod_estimate, ymin = prod_ci.lb, ymax = prod_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(logged~trimming)+
  scale_color_viridis(discrete=T)

rt_cdi_meta |> filter(window>300, window<600) |> ggplot(aes(x = type, y = prod_estimate, ymin = prod_ci.lb, ymax = prod_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(logged~trimming)+
  geom_hline(yintercept=-.3)+
  scale_color_viridis(discrete=T)
```
for production, numerically best is log, first_launch, trim_first at 400; but other options around there also work pretty well. 

## age
```{r}
rt_cdi_meta |> filter(window!=1000) |> ggplot(aes(x = type, y = age_estimate, ymin = age_ci.lb, ymax = age_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(logged~trimming)+
  scale_color_viridis(discrete=T)

rt_cdi_meta |> filter( window<600) |> ggplot(aes(x = type, y = age_estimate, ymin = age_ci.lb, ymax = age_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(logged~trimming)+
  geom_hline(yintercept=-.2)+
  scale_color_viridis(discrete=T)
```
## by age

```{r}
rt_cdi_age <- readRDS(here("cached_intermediates/3_rt_cdi_boot_byage.rds")) |> regroup_rt()
rt_cdi_meta_age <- rt_cdi_age |> do_cdi_meta(c("window", "time_0", "time_end", "during", "frac", "logged", "type", "trimming", "age_bin"))
```

### comp
```{r}
rt_cdi_meta_age |> filter(logged=="log") |> filter(!is.na(comp_estimate)) |>  filter(window>300, window<600) |> ggplot(aes(x = type, y = comp_estimate, ymin = comp_ci.lb, ymax = comp_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(trimming~age_bin)+
  geom_hline(yintercept=-.25)+
  scale_color_viridis(discrete=T)
```
### prod
```{r}
rt_cdi_meta_age |> filter(logged=="log") |> filter(!is.na(prod_estimate)) |>  filter(window>300, window<600) |> ggplot(aes(x = type, y = prod_estimate, ymin = prod_ci.lb, ymax = prod_ci.ub, color=as.character(window))) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +facet_grid(trimming~age_bin)+
  geom_hline(yintercept=-.25)+
  scale_color_viridis(discrete=T)
```


# TRT

```{r}
rt_trt <- readRDS(here("cached_intermediates/3_rt_test_retest_boot.rds")) |> regroup_rt()

rt_trt_meta <- rt_trt |> do_meta(c("window", "time_0", "time_end", "during", "frac", "type", "logged", "trimming"))
```



```{r}
  rt_trt_meta |> ggplot(aes(y = estimate, color = window, group=window, x = type, ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_grid(logged~trimming)+
  geom_hline(yintercept = .3) +
  scale_color_viridis(discrete = F)

  rt_trt_meta |> filter(window<600) |> ggplot(aes(y = estimate, color = window, group=window, x = type, ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_grid(logged~trimming)+
  geom_hline(yintercept = .35) +
  scale_color_viridis(discrete = F)

```

```{r}
 rt_trt |> filter(logged=="log", trimming=="untrimmed", window<600) |> ggplot(aes(y = est, color = window, group=window, x = type, ymin = lower, ymax = upper)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_grid(~dataset_name)+
  geom_hline(yintercept = 0) +
  scale_color_viridis(discrete = F)
```

# weird

so, how essential is it they their eyeballs be glued to the distractor? is a little wandering into other/NA okay?

```{r}
weird_icc <- readRDS(here("cached_intermediates/3_rt_icc_boot.rds")) |> filter(window==400, measure %in% c("land_rt", "log_land_rt")) |> do_meta(c("time_0", "time_end", "frac", "measure"))

weird_cdi <- readRDS(here("cached_intermediates/3_rt_cdi_boot_weird.rds")) |> 
  filter(window==400, measure %in% c("land_rt", "log_land_rt"))|> do_cdi_meta(c("time_0", "time_end", "frac", "measure"))

weird_trt <- readRDS(here("cached_intermediates/3_rt_test_retest_boot_weird.rds")) |> 
  filter(window==400, measure %in% c("land_rt", "log_land_rt"))|> do_meta(c("time_0", "time_end", "frac", "measure"))
```


```{r}
weird_icc |>  
  ggplot(aes(y = estimate, color = as.character(frac), group=interaction(frac, time_0, time_end), x = str_c("start:", time_0, ", end:", time_end), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~measure) +
  geom_hline(yintercept = .7) +
  scale_color_viridis(discrete = T)
```

```{r}
weird_cdi |>  
  ggplot(aes(y = comp_estimate, color = as.character(frac), group=interaction(frac, time_0, time_end), x = str_c("start:", time_0, ", end:", time_end), ymin = comp_ci.lb, ymax = comp_ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~measure) +
  geom_hline(yintercept = -.25) +
  scale_color_viridis(discrete = T)
```
```{r}
weird_cdi |>  
  ggplot(aes(y = prod_estimate, color = as.character(frac), group=interaction(frac, time_0, time_end), x = str_c("start:", time_0, ", end:", time_end), ymin = prod_ci.lb, ymax = prod_ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~measure) +
  geom_hline(yintercept = -.25) +
  scale_color_viridis(discrete = T)
```
```{r}
weird_trt |>  
  ggplot(aes(y = estimate, color = as.character(frac), group=interaction(frac, time_0, time_end), x = str_c("start:", time_0, ", end:", time_end), ymin = ci.lb, ymax = ci.ub)) +
  geom_pointrange(position=position_dodge(width=.5)) +
  coord_flip() +
  facet_wrap(~measure) +
  geom_hline(yintercept = -.25) +
  scale_color_viridis(discrete = T)
```


# Summary

I think our biggest takeaway is that it makes sense to do slightly longer windows more on the 375-400 ms than shorter windows like 200ms. 

Landing RT (with no exclusions for shift length) is slightly better in terms of ICC than launch based RT (with shift length exclusions), and they are pretty equivalent for CDI comparisons and test-retest. 

Depending on data pre-processing, if there's a little missing data in the 0-400ms window, it's probably okay to include (but this occurs rarely here). 

Overall, the range of common and reasonable choices lead to reasonable results. 
