---
title: "Exclusions"
author: "Mike Frank"
date: "2022-12-15"
output: html_document
---

Goal: consider consequences for reliability of exclusion decisions related to data quantity and behavior.

```{r}
source(here::here("helper/common.R"))
```


There's a lot of missing data and a lot of "zoners" (kids who look only at one side). Zoners are not just missing data kids.

```{r}
d_summary <- d_trial |>
  group_by(dataset_name, trial_id, dataset_id, subject_id, administration_id, 
           target_label) |>
  summarise(total_prop_target_looking = mean(correct, na.rm=TRUE),
            pre_prop_target_looking = mean(correct[t_norm < 300], na.rm=TRUE),
            prop_data = mean(!is.na(correct))) 
```

Plot total proportion target looking.

```{r}
ggplot(d_summary,
       aes(x = total_prop_target_looking)) + 
  geom_histogram()
```

In the pre-onset period. 

```{r}
ggplot(d_summary,
       aes(x = pre_prop_target_looking)) + 
  geom_histogram()
```

Plot total proportion of data

```{r}
ggplot(d_summary,
       aes(x = prop_data)) + 
  geom_histogram()
```

Break this down by dataset. 

```{r}
ggplot(d_summary,
       aes(x = prop_data)) + 
  geom_histogram() + 
  facet_wrap(~dataset_name, scales = "free_y")
```



# Exclusions simulation

Set up our measures for the simulation. 

```{r}
d_sim <- d_trial |>
  group_by(dataset_name, trial_id, dataset_id, subject_id, administration_id, 
           target_label) |>
  summarise(total_target_prop = mean(correct, na.rm=TRUE),
            prop_data = mean(!is.na(correct)), 
            accuracy = mean(correct[t_norm > 300 & t_norm < 4000], na.rm=TRUE)) 
```



```{r}

icc_sim <- function (zoners_included, exclude_less_than, object) 
{
  df <- d_sim |>
    filter(prop_data > exclude_less_than)
  
  # drop zoners
  if (zoners_included == FALSE) { 
    df <- filter(df, total_target_prop > 0, total_target_prop < 1) 
  }
  
  # compute ICCs
  df |> 
    group_by(dataset_name) |> 
    nest() |>
    mutate(icc = unlist(map(data, ~get_icc(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c()) 
}

```



# Exclusions based on zoners



Try to do this programmatically across all datasets.  

```{r, eval= FALSE, error=FALSE, message=FALSE, warning=FALSE}
excl_params <- expand_grid(zoners_included = c(FALSE, TRUE),
                           exclude_less_than = c(.1, .3, .5, .7, .9), 
                           object = c("stimulus", "administration")) |>
  mutate(icc = pmap(list(zoners_included, exclude_less_than, object), icc_sim)) |>
  unnest(col = icc)

save(excl_params, file = "cached_intermediates/3_exclusions.Rds")
```

Plot resulting ICCs.

```{r}
load("cached_intermediates/3_exclusions.Rds")

ggplot(excl_params,
       aes(x = exclude_less_than, y = icc, 
           group = interaction(dataset_name, zoners_included), 
           col = zoners_included)) + 
  geom_jitter(alpha = .3, width = .03) + 
  geom_line(alpha = .3) + 
  geom_smooth(aes(group = zoners_included), method = "lm") + 
  facet_grid(.~object) + 
  ylab("ICC") + 
  xlab("Include trials with more than")

```

Looks to me like excluding zoners isn't a clear win (and a loss for stimulus ICC). Further, excluding on amount of data doesn't seem to gain us reliability. 

