---
title: "Exclusions"
author: "Mike Frank"
date: "2022-12-15"
output: html_document
---

Goal: consider consequences for reliability of exclusion decisions related to data quantity and behavior.

Need to analyze both RT and accuracy. 

```{r}
source(here::here("helper/common.R"))

d_aoi <- readRDS(here("cached_intermediates", "0_d_aoi.rds"))
```

# Descriptive data 

Let's start with accuracy for descriptive data. 

There's a lot of missing data and a lot of "zoners" (kids who look only at one side). Zoners are not just missing data kids, they look in one direction for the entire trial. 

```{r}
d_summary <- d_aoi |>
  group_by(
    dataset_name, trial_id, dataset_id, subject_id, administration_id, target_side,
    target_label
  ) |>
  summarise(
    total_prop_target_looking = mean(correct, na.rm = TRUE),
    pre_prop_target_looking = mean(correct[t_norm < 400], na.rm = TRUE),
    prop_data = mean(!is.na(correct))
  )
```

## Trial-wise

Plot total proportion target looking.

```{r}
ggplot(
  d_summary,
  aes(x = total_prop_target_looking)
) +
  geom_histogram()
```

In the pre-onset period. 

```{r}
ggplot(
  d_summary,
  aes(x = pre_prop_target_looking)
) +
  geom_histogram()
```

Plot total proportion of data

```{r}
ggplot(
  d_summary,
  aes(x = prop_data)
) +
  geom_histogram()
```

Break this down by dataset. 

```{r}
ggplot(
  d_summary,
  aes(x = prop_data)
) +
  geom_histogram() +
  facet_wrap(~dataset_name, scales = "free_y")
```

Some datasets have already been filtered for missing data. Others have not. 

## Kid-wise

We can also look at the proportion of data per kid. 

```{r}
d_bykid_summary <- d_summary |>
  group_by(dataset_name, administration_id) |>
  summarise(
    total_prop_target_looking =
      mean(total_prop_target_looking, na.rm = TRUE),
    n_trials = length(unique(trial_id[prop_data > 0])),
    prop_data = mean(prop_data, na.rm = TRUE)
  )
```

```{r}
ggplot(d_bykid_summary, aes(x = prop_data)) +
  geom_histogram()
```

Looking at targets. 

```{r}
ggplot(d_bykid_summary, aes(x = total_prop_target_looking)) +
  geom_histogram()
```
# Accuracy Trial-exclusions
trial-wise:
* prop data in the trial
* only looking at one side in the trial (trial-zoning)
* pre-target word zoning vs. post-target word zoning

## Bootstrapped ICC


```{r}
trial_boot <- readRDS(here("cached_intermediates/4_acc_trial_icc_boot.rds")) |> unnest(num_trials) |>  group_by(dataset_name, t_start, t_end) |> 
  mutate(pct=num_trials/max(num_trials))
```




```{r}
trial_boot |> ggplot(aes(x = exclude_less_than, y = est, color = pct, group=interaction(look_both, t_end))) +
  geom_point() +
  geom_line()+
  scale_color_viridis(option="inferno")+
  facet_wrap(~dataset_name)+theme(legend.position = "bottom")
```
this is pretty hard to interpret, so we calculate meta-analytic means and ranges for each condition. 

```{r}
library(metafor)
trial_boot_summary <- trial_boot |>
  filter(!is.na(lower), !is.na(upper)) |>
  mutate(
    stdev = (upper - lower) / (1.96 * 2),
    var = stdev**2
  ) |>
  group_by(t_start, t_end, exclude_less_than, look_both) |>
  nest() |>
  mutate(icc = map(data, \(d){
    rma(d$est, d$var) |>
      summary() |>
      coef()
  }),
  n=map(data, \(d) sum(d$num_trials))) |>
  select(-data) |>
  unnest(icc) |> 
  unnest(n) |> 
  group_by(t_end) |> 
  mutate(n=n/max(n))

```

Looking overall

```{r}
trial_boot_summary |> ggplot(aes(x = exclude_less_than, y = estimate, ymin = ci.lb, ymax = ci.ub, color = n)) +
  geom_pointrange(position=position_dodge(.05))+facet_wrap(~t_end~look_both)+  scale_color_viridis(option="inferno")


trial_boot_summary |> filter(exclude_less_than<.6) |> ggplot(aes(x =n, y = estimate, ymin = ci.lb, ymax = ci.ub, color = exclude_less_than)) +
  geom_pointrange(position=position_dodge(.05))+facet_wrap(~t_end)+scale_color_viridis()
```

it's not necessarily crazy to exclude kids who contribute extremely little, also doesn't help that much?

### by age

```{r}
trial_boot_age <- readRDS(here("cached_intermediates/4_acc_trial_icc_boot_byage.rds")) |> unnest(num_trials) |>  group_by(dataset_name, t_start, t_end, age_bin) |> 
  mutate(pct=num_trials/max(num_trials))
```


```{r}
library(metafor)
trial_boot_summary_age <- trial_boot_age |>
  filter(!is.na(lower), !is.na(upper)) |>
  mutate(
    stdev = (upper - lower) / (1.96 * 2),
    var = stdev**2
  ) |>
  group_by(t_start, t_end, exclude_less_than, look_both, age_bin) |>
  nest() |>
  mutate(icc = map(data, \(d){
    rma(d$est, d$var) |>
      summary() |>
      coef()
  }),
  n=map(data, \(d) sum(d$num_trials))) |>
  select(-data) |>
  unnest(icc) |> 
  unnest(n) |> 
  group_by(t_end, age_bin) |> 
  mutate(n=n/max(n))

```

Looking overall

```{r}
trial_boot_summary_age |> ggplot(aes(x = exclude_less_than, y = estimate, ymin = ci.lb, ymax = ci.ub, color = n)) +
  geom_pointrange(position=position_dodge(.05))+facet_wrap(~age_bin~t_end~look_both)+  scale_color_viridis(option="inferno")


trial_boot_summary_age |> filter(exclude_less_than<.6) |> filter(look_both!="before") |> ggplot(aes(x =n, y = estimate, ymin = ci.lb, ymax = ci.ub, color = exclude_less_than)) +
  geom_pointrange(position=position_dodge(.05))+facet_wrap(age_bin~t_end)+scale_color_viridis()
```

slight, continuous trade-offs between ICC and how many trials are kept -- primarily driven by the older kids? 



## CDI corr

Reliability measures like ICC tell us how consistently we're measuring *something*, but they don't tell us what the *something* we're measuring is. For that, we want a check on validity, so we look at the correlation between accuracy (measured on different windows) with each of CDI production measures, CDI comprehension measures, and age. 



```{r}
trial_cdi <- readRDS(here("cached_intermediates", "4_acc_trial_cdi_boot.rds"))

trial_cdi_summ <-  trial_cdi |> do_cdi_meta(c("t_end", "look_both", "exclude_less_than", "look_both"))


```

Correlation with comprehension

```{r}
trial_cdi_summ  |> ggplot(aes(x = exclude_less_than, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=look_both)) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~t_end)+geom_hline(yintercept=.2)

```
don't do look-before; no need to do exclude less than, it doesn't help and may make things worse (but up to .5 seems fine)

Correlation with production

```{r}
trial_cdi_summ  |> ggplot(aes(x = exclude_less_than, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=look_both)) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~t_end)+geom_hline(yintercept=.3)

```
no need on the looking at both; excluding trials with very little data is fine, although of unclear utility


### by age 

Reliability measures like ICC tell us how consistently we're measuring *something*, but they don't tell us what the *something* we're measuring is. For that, we want a check on validity, so we look at the correlation between accuracy (measured on different windows) with each of CDI production measures, CDI comprehension measures, and age. 



```{r}
trial_cdi_age <- readRDS(here("cached_intermediates", "4_acc_trial_cdi_boot_byage.rds"))

trial_cdi_summ_age <-  trial_cdi_age |> do_cdi_meta(c("t_end", "look_both", "exclude_less_than", "look_both", "age_bin"))


```

Correlation with comprehension

```{r}
trial_cdi_summ_age  |> filter(t_end=="3000") |> filter(!is.na(comp_estimate)) |> ggplot(aes(x = exclude_less_than, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=look_both)) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~age_bin)+geom_hline(yintercept=.2)

```
don't do look-before; no need to do exclude less than, it doesn't help and may make things worse (but up to .5 seems fine)

Correlation with production

```{r}
trial_cdi_summ_age  |>filter(t_end=="3000") |>filter(!is.na(prod_estimate)) |>   ggplot(aes(x = exclude_less_than, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=look_both)) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~age_bin)+geom_hline(yintercept=.3)

```
no need on the looking at both; excluding trials with very little data is fine, although of unclear utility



## Test retest


```{r}
trial_test_retest <- readRDS(here("cached_intermediates", "4_acc_trial_test_retest_boot.rds"))

trial_test_retest_summ <-  trial_test_retest |>do_meta(c("t_end", "exclude_less_than", "look_both"))
```


```{r}
trial_test_retest |> ggplot(aes(x=exclude_less_than, y=est, ymin=lower, ymax=upper, color=look_both))+geom_pointrange(position = position_dodge(width=.05))+facet_grid(t_end~dataset_name)+geom_hline(yintercept=0)+coord_flip()
```


```{r}
trial_test_retest_summ |> ggplot(aes(x=exclude_less_than, y=estimate, ymin=ci.lb, ymax=ci.ub, color=look_both))+geom_pointrange(position = position_dodge(width=.05))+geom_hline(yintercept=.5)+facet_wrap(~t_end)+coord_flip()

```


again, no need to exclude, excluding nothing pretty comparable to doing some exclusions, up to 50%. 
# TODO accuracy kid exclusions

## Bootstrapped ICC


```{r}
kid_acc_icc <- readRDS(here("cached_intermediates/4_acc_kid_icc_boot.rds")) 

kid_acc_icc_summ <- kid_acc_icc |> do_meta(c("t_start", "t_end", "min_trial", "exclude_less_than"))
```



Looking overall

```{r}


kid_acc_icc_summ |> ggplot(aes(x = min_trial, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.factor(exclude_less_than))) +
  geom_pointrange(position=position_dodge(.5))+facet_wrap(~t_end)+scale_color_viridis(discrete=T)+coord_flip()+geom_hline(yintercept=.4)
```
min trial cutoffs mostly don't seem effective for ICC

### by age

```{r}
kid_acc_icc_age <- readRDS(here("cached_intermediates/4_acc_kid_icc_boot_byage.rds")) 

kid_acc_icc_summ_age <- kid_acc_icc_age |> do_meta(c("t_start", "t_end", "min_trial", "exclude_less_than", "age_bin"))
```



Looking overall

```{r}


kid_acc_icc_summ_age |> filter(t_end=="3000") |> ggplot(aes(x = min_trial, y = estimate, ymin = ci.lb, ymax = ci.ub, color = as.factor(exclude_less_than))) +
  geom_pointrange(position=position_dodge(.5))+facet_wrap(~age_bin)+scale_color_viridis(discrete=T)+coord_flip()+geom_hline(yintercept=.4)
```

## CDI corr


```{r}
kid_cdi <- readRDS(here("cached_intermediates", "4_acc_kid_cdi_boot.rds")) |> filter(min_trial<11)

kid_cdi_summ <-  kid_cdi |> do_cdi_meta(c("t_end", "look_both", "exclude_less_than", "look_both", "min_trial"))


```

Correlation with comprehension

```{r}
kid_cdi_summ  |> ggplot(aes(x = min_trial, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.factor(exclude_less_than))) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~t_end)+geom_hline(yintercept=.2)+scale_color_viridis(discrete=T)

```
possible argument for min of 3-4 trials??


Correlation with production

```{r}
kid_cdi_summ  |> ggplot(aes(x = min_trial, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.factor(exclude_less_than))) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~t_end)+geom_hline(yintercept=.3)+scale_color_viridis(discrete=T)

```
reasonable to do like min 5?

### by age 

```{r}
kid_cdi_age <- readRDS(here("cached_intermediates", "4_acc_kid_cdi_boot_byage.rds")) |> filter(min_trial<11)

kid_cdi_summ_age <-  kid_cdi_age |> do_cdi_meta(c("t_end", "look_both", "exclude_less_than", "look_both", "min_trial", "age_bin"))


```

Correlation with comprehension

```{r}
kid_cdi_summ_age  |> filter(t_end=="3000") |> filter(!is.na(comp_estimate)) |> ggplot(aes(x = min_trial, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.factor(exclude_less_than))) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~age_bin)+geom_hline(yintercept=.2)+scale_color_viridis(discrete=T)

```
```{r}
kid_cdi_summ_age  |> filter(t_end=="3000") |> filter(!is.na(prod_estimate)) |> ggplot(aes(x = min_trial, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.factor(exclude_less_than))) +geom_pointrange(position=position_dodge(width=.05))+coord_flip()+facet_wrap(~age_bin)+geom_hline(yintercept=.2)+scale_color_viridis(discrete=T)

```
## Test retest


```{r}
kid_test_retest <- readRDS(here("cached_intermediates", "4_acc_kid_test_retest_boot.rds"))

kid_test_retest_summ <-  kid_test_retest |>do_meta(c("t_end", "exclude_less_than", "look_both", "min_trial"))
```


```{r}
kid_test_retest |> ggplot(aes(x=min_trial, y=est, ymin=lower, ymax=upper))+geom_pointrange(position = position_dodge(width=.05))+geom_hline(yintercept=0)+coord_flip()+geom_smooth()
```


```{r}
kid_test_retest_summ |> ggplot(aes(x=min_trial, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.factor(exclude_less_than)))+geom_pointrange(position = position_dodge(width=.5))+geom_hline(yintercept=.5)+facet_wrap(~t_end)+coord_flip()+geom_smooth()

```
for T-RT is does get better with more trials, at least up to 5 and maybe 8. 


# TODO RT Kid exclusions

## Bootstrapped ICC

TODO after we get the re-run version!

```{r}
rt_icc <- readRDS(here("cached_intermediates/4_rt_icc_boot.rds"))

rt_icc_summ <- rt_icc |> do_meta(c("window", "time_0", "time_end", "during", "frac", "type", "logged","trimming", "min_trial"))
```


### by age


## CDI corr


```{r}
kid_cdi <- readRDS(here("cached_intermediates", "4_rt_cdi_boot.rds")) |> regroup_rt()

kid_cdi_summ <-  kid_cdi |> do_cdi_meta(c("window", "time_0", "time_end", "during", "frac", "type", "logged","trimming", "min_trial"))


```

Correlation with comprehension

```{r}
kid_cdi_summ  |> filter(logged=="log") |> ggplot(aes(x =min_trial, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=str_c(type,"_" , trimming)))+ geom_pointrange(position=position_dodge(width=.5))+coord_flip()+geom_hline(yintercept=-.2)+facet_wrap(type~trimming)

```
2 trial is reasonable? 

Correlation with production
```{r}
kid_cdi_summ  |> filter(logged=="log") |> ggplot(aes(x =min_trial, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=str_c(type,"_" , trimming)))+ geom_pointrange(position=position_dodge(width=.5))+coord_flip()+geom_hline(yintercept=-.35)+facet_wrap(type~trimming)

```
2 trials is reasonable; more is better (but have to balance against data loss) 

### by age 
```{r}
kid_cdi_age <- readRDS(here("cached_intermediates", "4_rt_cdi_boot_byage.rds")) |> regroup_rt()

kid_cdi_summ_age <-  kid_cdi_age |> do_cdi_meta(c("window", "time_0", "time_end", "during", "frac", "type", "logged","trimming", "min_trial", "age_bin"))


```

Correlation with comprehension

```{r}
kid_cdi_summ_age  |> filter(logged=="log", trimming=="untrimmed", type=="land") |> 
  filter(!is.na(comp_estimate))|> ggplot(aes(x =min_trial, y = comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=str_c(type,"_" , trimming)))+ geom_pointrange(position=position_dodge(width=.5))+coord_flip()+geom_hline(yintercept=-.2)+facet_wrap(~age_bin)

```
2 trial is reasonable? 

Correlation with production
```{r}
kid_cdi_summ_age  |> filter(logged=="log", trimming=="untrimmed", type=="land") |> 
  filter(!is.na(prod_estimate))|> ggplot(aes(x =min_trial, y = prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=str_c(type,"_" , trimming)))+ geom_pointrange(position=position_dodge(width=.5))+coord_flip()+geom_hline(yintercept=-.3)+facet_wrap(~age_bin)

```
2 trials is reasonable; more is better (but have to balance against data loss) 


## Test retest


```{r}
rt_test_retest <- readRDS(here("cached_intermediates", "4_rt_test_retest_boot.rds")) |> regroup_rt() |> 
  filter(dataset_name!="potter_remix")

rt_test_retest_summ <-  rt_test_retest |> do_meta(c("window", "time_0", "time_end", "during", "frac", "type", "logged","trimming", "min_trial"))
```


```{r}
rt_test_retest |> filter(logged=="log", trimming=="untrimmed", type=="land") |> ggplot(aes(x=min_trial, y=est, ymin=lower, ymax=upper, color=dataset_name))+geom_pointrange(position = position_dodge(width=.5))+geom_hline(yintercept=0)+coord_flip()+geom_line()
```


```{r}
rt_test_retest_summ |> filter(logged=="log", trimming=="untrimmed", type=="land") |> ggplot(aes(x=min_trial, y=estimate, ymin=ci.lb, ymax=ci.ub))+geom_pointrange(position = position_dodge(width=.05))+geom_hline(yintercept=.5)+coord_flip()

```

1 to 2 makes a big difference? again check against dataloss

# Summary
For acc -- there's no need to do look both ways exclusions (we're not crossing streets), it is reasonable, although not clearly beneficial, to do exclude trials with less than .5 (or more lax) time points. For number of trials, more trials is better, which trades off against data loss (because you lose power/generalizability). These gains are slightly seen in CDI (slight improvement up to like 5 trials), and are seen in test-retest up to 5-8 trials. But that's also fewer kids!

For RT, we don't yet know about ICC, but for CDI and TRT, two trials is better than one (and possibly more beyond that, but you trade off against fewer kids). 


