---
title: "Simulate number of trials"
author: "Veronica"
date: "2026-03-06"
output: html_document
---

```{r}
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))
```

# Acc - Downsampling

Our goal is to determine how different number of hypothetical trials would impact the measure we care about, especially T-RT. 

One way to look at this is by down-sampling for kids who had more than a threshold of trials

## T-RT
```{r}
downsample_trt <- readRDS(here("cached_intermediates/5_acc_downsample_test_retest_boot.rds"))
downsample_trt_summ <- downsample_trt |> do_meta(c("t_start", "t_end", "sample_down", "start_point"))

```

```{r}

downsample_trt |> filter(t_end==3000) |> ggplot(aes(x=sample_down, y=est, ymin=lower, ymax=upper, color=as.character(dataset_name), group=interaction(t_start, t_end, start_point, dataset_name)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~start_point)+theme(legend.position = "bottom")
```
```{r}
downsample_trt_summ |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~t_end)+theme(legend.position = "bottom")
```
maybe benefits diminish after like 10? trials. 



# RT - Downsampling

Our goal is to determine how different number of hypothetical trials would impact the measure we care about, especially T-RT. 


One way to look at this is by down-sampling for kids who had more than a threshold of trials

## T-RT
```{r}
downsample_trt <- readRDS(here("cached_intermediates/5_rt_test_retest_boot.rds")) |> regroup_rt() |> 
  filter(!is.na(est)) |> filter(start_point!=15)
downsample_trt_summ <- downsample_trt |> do_meta(c("type", "logged", "trimming", "sample_down", "start_point"))

```

```{r}

downsample_trt |> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=est, ymin=lower, ymax=upper))+geom_pointrange(aes(color=as.character(dataset_name), group=interaction(type, logged, trimming, start_point, dataset_name)))+geom_line(aes(color=as.character(dataset_name), group=interaction(type, logged, trimming, start_point, dataset_name)))+geom_smooth()+geom_hline(yintercept=0)+facet_grid(logged~start_point)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(-1, 1))
```
```{r}
downsample_trt_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~logged)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(-1, 1))
```
```{r}
downsample_trt_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_hline(yintercept=0)+facet_grid(logged~start_point)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(-1, 1))
```
RT -- as many as you can get is better -- up to 7, beyond that we don't have dense enough data to know. But note that 7 RT is like 20+ trials 
