---
title: "Simulate number of trials"
author: "Veronica"
date: "2026-03-06"
output: html_document
---

```{r}
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))
```

# Acc - Downsampling

Our goal is to determine how different number of hypothetical trials would impact the measure we care about, especially T-RT. 

One way to look at this is by down-sampling for kids who had more than a threshold of trials


## T-RT
```{r}
downsample_trt <- readRDS(here("cached_intermediates/5_acc_downsample_test_retest_boot.rds"))


#downsample_trt_summ <- downsample_trt |> do_meta(c("t_start", "t_end", "sample_down", "start_point"))

```

```{r}

downsample_trt |> filter(t_end==3000) |> ggplot(aes(x=sample_down, y=est, ymin=lower, ymax=upper, color=as.character(dataset_name), group=interaction(t_start, t_end, start_point, dataset_name)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~start_point)+theme(legend.position = "bottom")
```
```{r}
downsample_trt_summ |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~t_end)+theme(legend.position = "bottom")
```
maybe benefits diminish after like 10? trials. 

## ICC
```{r}
downsample_icc <- readRDS(here("cached_intermediates/5_acc_icc_boot.rds"))
downsample_icc_summ <- downsample_icc |> do_meta(c("t_start", "t_end", "sample_down", "start_point"))

```

```{r}
downsample_icc_summ |> filter(t_end==3000) |>  ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_hline(yintercept=0)+facet_grid(~t_end)+theme(legend.position = "bottom")
```
not meaningful effects 

## CDI

```{r}
downsample_cdi <- readRDS(here("cached_intermediates/5_acc_cdi_boot.rds"))
downsample_cdi_summ <- downsample_cdi |> do_cdi_meta(c("t_start", "t_end", "sample_down", "start_point"))

```


```{r}
downsample_cdi_summ |> filter(t_end==3000) |> ggplot(aes(x=sample_down, y=comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+theme(legend.position = "bottom")

downsample_cdi_summ |> filter(t_end==3000) |> ggplot(aes(x=sample_down, y=comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_hline(yintercept=0)+theme(legend.position = "bottom")+facet_wrap(~start_point)
```
correlation with comp gets better up to 10; unclear thereafter


```{r}
downsample_cdi_summ |> filter(t_end==3000) |> ggplot(aes(x=sample_down, y=prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+theme(legend.position = "bottom")

downsample_cdi_summ |> filter(t_end==3000) |> ggplot(aes(x=sample_down, y=prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(start_point), group=interaction(t_start, t_end, start_point)))+geom_pointrange()+geom_line()+geom_hline(yintercept=0)+theme(legend.position = "bottom")+facet_wrap(~start_point)
```
also broadly supports a gains til around 10, then less clear

# RT - Downsampling

Our goal is to determine how different number of hypothetical trials would impact the measure we care about, especially T-RT. 


One way to look at this is by down-sampling for kids who had more than a threshold of trials

## T-RT
```{r}
downsample_trt <- readRDS(here("cached_intermediates/5_rt_test_retest_boot.rds")) |> regroup_rt() |> 
  filter(!is.na(est)) |> filter(start_point!=15)
downsample_trt_summ <- downsample_trt |> do_meta(c("type", "logged", "trimming", "sample_down", "start_point"))

```

```{r}

downsample_trt |> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=est, ymin=lower, ymax=upper))+geom_pointrange(aes(color=as.character(dataset_name), group=interaction(type, logged, trimming, start_point, dataset_name)))+geom_line(aes(color=as.character(dataset_name), group=interaction(type, logged, trimming, start_point, dataset_name)))+geom_smooth()+geom_hline(yintercept=0)+facet_grid(logged~start_point)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(-1, 1))
```
```{r}
downsample_trt_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~logged)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(-1, 1))
```
```{r}
downsample_trt_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_hline(yintercept=0)+facet_grid(logged~start_point)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(-1, 1))
```
RT -- as many as you can get is better -- up to 7, beyond that we don't have dense enough data to know. But note that 7 RT is like 20+ trials 

## ICC
```{r}
downsample_rt_icc <- readRDS(here("cached_intermediates/5_rt_icc_boot.rds")) |> regroup_rt() |> 
  filter(!is.na(est)) |> filter(start_point!=15)
downsample_rt_icc_summ <- downsample_rt_icc |> do_meta(c("type", "logged", "trimming", "sample_down", "start_point"))

```

```{r}
downsample_rt_icc_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=estimate, ymin=ci.lb, ymax=ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~logged)+theme(legend.position = "bottom")+coord_cartesian(ylim=c(0, 1))
```

## CDI 

```{r}
downsample_rt_cdi <- readRDS(here("cached_intermediates/5_rt_cdi_boot.rds")) |> regroup_rt() |> filter(start_point!=15)
downsample_rt_cdi_summ <- downsample_rt_cdi|> do_cdi_meta(c("type", "logged", "trimming", "sample_down", "start_point"))

```

```{r}
downsample_rt_cdi_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=comp_estimate, ymin=comp_ci.lb, ymax=comp_ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~logged)+theme(legend.position = "bottom")
```

definitely some error bars, but having like 3+ is better than having less? 

```{r}
downsample_rt_cdi_summ|> filter(trimming=="untrimmed", type=="land") |> ggplot(aes(x=sample_down, y=prod_estimate, ymin=prod_ci.lb, ymax=prod_ci.ub, color=as.character(start_point), group=interaction(type, logged, trimming, start_point)))+geom_pointrange()+geom_line()+geom_smooth(aes(group=1))+geom_hline(yintercept=0)+facet_grid(~logged)+theme(legend.position = "bottom")
```

so like 3 or 4 minimum??


# Summary

For ICC reliability, there isn't that much sensitivity to number of trials per subject. 

For accuracy trials, having more trials per session increases t-rt reliability up to at least 10 trials, and (at a lower rate) above that. For reliable accuracy measures of individual children/differences, use at least 10 trials / condition. 

For comparison with CDI, definitely at least 10 trials, more is probably better, but the biggest gains are early on. (much much better to have 5 than 1). 

For RT, TRT definitely gains to 5 -- gets a lot harder to measure after that since there are fewer valid pairs. But probably 7 is better than 5.For CDI measures, again high uncertainty, but seem to be gains for having 4 trials? (which means 12+)

If you want stable individual differences of RT, as many trials as possible is important, we recommend aiming for 20 to try to end up with an average around 7 per child, as roughly 1/3 of trials will have a valid RT (other approaches such as gaze-triggering might also be possibilities for increasing the rate of valid RTs). Reasonable correlation with CDI can be reached with 4-5 trials. Hard to say much about benefits of even more trials because there aren't that many kids in the data we have with more trials / session. 


