---
title: "Number of trials"
author: "Mike Frank"
date: "2022-12-15"
output: html_document
---

```{r}
source(here::here("helper/common.R"))
```

Goal is to find out how reliability (test-retest and ICC) varies with number of trials, both within and across datasets. 

Want to look at test-retest in totlot (FM 2012) and Adams Marchman (2018) because we have that. 

Look at condition differences across datasets

# Across datasets - n observations

Let's start by looking at number of trials per kid/per item as a predictor of ICC across datasets. 

```{r}
d_n_trial_sim <- d_trial |>
  group_by(dataset_name, trial_id, dataset_id, subject_id, administration_id,
           age, target_label) |>
  summarise(accuracy = mean(correct[t_norm > 300 & t_norm < 4000], na.rm=TRUE)) 
```

Now our simulation. 

```{r}
get_n_trials <- function (x, column = "accuracy", 
                          object = "stimulus") {
  if (object == "stimulus") {
    n_trials <- x |>
      group_by(target_label) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  } else {
    n_trials <- x |>
      group_by(administration_id) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  }
  
  return(n_trials)
}

icc_n_trial_sim <- function (object) 
{
  # compute ICCs
  d_n_trial_sim |> 
    group_by(dataset_name) |> 
    nest() |>
    mutate(icc = unlist(map(data, ~get_icc(., "accuracy", object))),
           n_trials = unlist(map(data, ~get_n_trials(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c()) 
}

```


```{r, eval= FALSE, error=FALSE, message=FALSE, warning=FALSE}
n_trial_params <- expand_grid(object = c("stimulus", "administration"))

tic()
n_trial_sim <- n_trial_params |> 
  mutate(icc = pmap(list(object), 
                    icc_n_trial_sim)) |>
  unnest(col = icc)
toc()

save(n_trial_sim, file = "cached_intermediates/6_n_trials.Rds")
```

Plot resulting ICCs.

```{r}
load("cached_intermediates/6_n_trials.Rds")

ggplot(n_trial_sim,
       aes(x = n_trials, y = icc, col = dataset_name)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(col = NA, group = 1), se = FALSE) +
  geom_label_repel(aes(label = dataset_name), size = 1) +
  facet_wrap(~object, scales = "free_x") + 
  ylab("ICC") + 
  xlab("Number of observations per group") + 
  ggthemes::theme_few() + 
  theme(legend.position = "bottom") + 
  ylim(0,1)
```
# Resampling approach to this question

Lots of confounding in the above analysis - in particular, item variation and kid (age) variation

The best way to get at it would be to down (and perhaps up) sample the number of observations within a dataset. 


# Longitudinal data

What datasets have longitudinal data? Just Adams Marchman and FMW.

```{r}
longitudinal <- d_n_trial_sim |>
  group_by(dataset_name) |>
  summarise(n_admins = length(unique(administration_id)), 
            n_subs = length(unique(subject_id))) |>
  filter(n_admins != n_subs) 
longitudinal
```

Get test-retest. 

For AM2018, kids were tested twice at each age. For pragmatic reasons, we use kids who have all four observations, which is all but 4 of them. 

For FMW, kids were OFTEN tested twice at the younger age. 

We should compute immediate test-retest for each of these. 

Could also compute T-RT over age/development for each but this is a different thing...


```{r}

complete_obs <- d_n_trial_sim |>
  filter(dataset_name %in% longitudinal$dataset_name) |>
  group_by(dataset_name, subject_id, administration_id) |> 
  count() |>
  group_by(dataset_name, subject_id) |>
  count() |>
  filter((dataset_name == "adams_marchman_2018" & n == 4) |
           (dataset_name == "fmw_2013" & n > 1))
  
  

admin_means <- d_n_trial_sim |>
  filter(subject_id %in% complete_obs$subject_id) |>
  group_by(dataset_name, subject_id, administration_id) |>
  summarise(accuracy = mean(accuracy, na.rm=TRUE), 
            age = age[1]) |>
  group_by(dataset_name, subject_id) |>
  mutate(age_group = ifelse(dataset_name == "adams_marchman_2018", 
                            c(1,1,2,2), c(1,1))) |>
  group_by(dataset_name, subject_id, age_group) |>
  mutate(test_session = 1:n()) |>
  select(-administration_id) |>
  pivot_wider(names_from = "test_session", values_from = "accuracy") |>
  rename(session1 = `1`, 
         session2 = `2`,
         session3 = `3`)

```

```{r}
ggplot(admin_means, aes(x = session1, y = session2)) +
  facet_wrap(~dataset_name) + 
  geom_point() + 
  geom_smooth(method = "lm")

admin_means |>
  group_by(dataset_name, age_group) |>
  nest() |>
  mutate(cor = lapply(data, 
                      function(df) {
                        s1 = df$session1 
                        s2 = df$session2
                        
                        broom::tidy(cor.test(x = s1, y = s2))
                        })) |>
  select(-data) |>
  unnest(cols = cor)
```



# Within dataset - n observations - NOT FIXED YET

Now let's take advantage of datasets with lots of trials per kid and see what we can do about subsampling to look at reliabilities over number of trials.

UNMODIFIED CODE BELOW

```{r}
get_n_trials <- function (x, column = "accuracy", object = "stimulus") {
  if (object == "stimulus") {
    n_trials <- x |>
      group_by(target_label) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  } else {
    n_trials <- x |>
      group_by(administration_id) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  }
  
  return(n_trials)
}

icc_sim <- function (object) 
{
  # compute ICCs
  d_sim |> 
    group_by(dataset_name) |> 
    nest() |>
    mutate(icc = unlist(map(data, ~get_icc(., "accuracy", object))),
           n_trials = unlist(map(data, ~get_n_trials(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c()) 
}

```


```{r, eval= FALSE, error=FALSE, message=FALSE, warning=FALSE}
iccs <- expand_grid(object = c("stimulus", "administration")) |>
  mutate(icc = pmap(list(object), icc_sim)) |>
  unnest(col = icc)

save(iccs, file = "cached_intermediates/6_n_trials.Rds")
```

Plot resulting ICCs.

```{r}
load("cached_intermediates/6_n_trials.Rds")

ggplot(iccs,
       aes(x = n_trials, y = icc, col = dataset_name)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(group = 1)) +
  geom_label_repel(aes(label = dataset_name)) + 
  facet_wrap(~object, scales = "free_x") + 
  ylab("ICC") + 
  xlab("Number of observations per group") + 
  ggthemes::theme_few() + 
  theme(legend.position = "bottom") 

```
