---
title: "Number of trials"
author: "Mike Frank"
date: "2022-12-15"
output: html_document
---

```{r}
source(here::here("helper/common.R"))
```

Goal is to find out how ICC varies with number of trials, both within and across datasets. 

Want to look at test-retest in totlot (FM 2012) and Adams Marchman (2018)

Look at condition differences across datasets

# Across datasets - n observations

Let's start by looking at number of trials per kid/per item as a predictor of ICC across datasets. 

```{r}
d_sim <- d_trial |>
  group_by(dataset_name, trial_id, dataset_id, subject_id, administration_id, 
           target_label) |>
  summarise(accuracy = mean(correct[t_norm > 300 & t_norm < 4000], na.rm=TRUE)) 
```

Now our simulation. 

```{r}
get_n_trials <- function (x, column = "accuracy", 
                          object = "stimulus") {
  if (object == "stimulus") {
    n_trials <- x |>
      group_by(target_label) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  } else {
    n_trials <- x |>
      group_by(administration_id) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  }
  
  return(n_trials)
}

icc_sim <- function (object) 
{
  # compute ICCs
  d_sim |> 
    group_by(dataset_name) |> 
    nest() |>
    mutate(icc = unlist(map(data, ~get_icc(., "accuracy", object))),
           n_trials = unlist(map(data, ~get_n_trials(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c()) 
}

```


```{r, eval= FALSE, error=FALSE, message=FALSE, warning=FALSE}
iccs <- expand_grid(object = c("stimulus", "administration")) |>
  mutate(icc = pmap(list(object), icc_sim)) |>
  unnest(col = icc)

save(iccs, file = "cached_intermediates/5_n_trials.Rds")
```

Plot resulting ICCs.

```{r}
load("cached_intermediates/5_n_trials.Rds")

ggplot(iccs,
       aes(x = n_trials, y = icc, col = dataset_name)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(group = 1)) +
  geom_label_repel(aes(label = dataset_name)) + 
  facet_wrap(~object, scales = "free_x") + 
  ylab("ICC") + 
  xlab("Number of observations per group") + 
  ggthemes::theme_few() + 
  theme(legend.position = "bottom") 

```


# Within dataset - n observations

Now let's take advantage of datasets with lots of trials per kid and see what we can do about subsampling to look at reliabilities over number of trials.

UNMODIFIED CODE BELOW

```{r}
get_n_trials <- function (x, column = "accuracy", object = "stimulus") {
  if (object == "stimulus") {
    n_trials <- x |>
      group_by(target_label) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  } else {
    n_trials <- x |>
      group_by(administration_id) |>
      count() |>
      ungroup() |>
      summarise(n_trials = mean(n)) |>
      pull(n_trials)
      
  }
  
  return(n_trials)
}

icc_sim <- function (object) 
{
  # compute ICCs
  d_sim |> 
    group_by(dataset_name) |> 
    nest() |>
    mutate(icc = unlist(map(data, ~get_icc(., "accuracy", object))),
           n_trials = unlist(map(data, ~get_n_trials(., "accuracy", object)))) |>
    select(-data) |>
    unnest(cols = c()) 
}

```


```{r, eval= FALSE, error=FALSE, message=FALSE, warning=FALSE}
iccs <- expand_grid(object = c("stimulus", "administration")) |>
  mutate(icc = pmap(list(object), icc_sim)) |>
  unnest(col = icc)

save(iccs, file = "cached_intermediates/5_n_trials.Rds")
```

Plot resulting ICCs.

```{r}
load("cached_intermediates/5_n_trials.Rds")

ggplot(iccs,
       aes(x = n_trials, y = icc, col = dataset_name)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(group = 1)) +
  geom_label_repel(aes(label = dataset_name)) + 
  facet_wrap(~object, scales = "free_x") + 
  ylab("ICC") + 
  xlab("Number of observations per group") + 
  ggthemes::theme_few() + 
  theme(legend.position = "bottom") 

```
