---
title: "Baseline correction"
author: "Mike Frank"
date: "2022-12-15"
output: html_document
---



```{r}
source(here::here("helper/common.R"))
```




# Measure 2: Baseline-corrected accuracy

For our next measure, we'll repeat the same exercise, but we'll baseline-corrected looking. Let's start by implementing baseline-correction in the simplest way possible. 

Zooming in on Adams-Marchman, since that had very high administration reliability. 

```{r}
qplot(data = filter(d_trial, 
                    dataset_name == "adams_marchman_2018"), 
      x = t_norm, geom = "histogram")
```

```{r}
am <- d_trial |>
  filter(dataset_name == "adams_marchman_2018") |>
  group_by(trial_id, subject_id, administration_id, 
           target_label) |>
  summarise(baseline = mean(correct[t_norm < 500], na.rm=TRUE),
            accuracy = mean(correct[t_norm > 500], na.rm=TRUE), 
            bc_accuracy = accuracy - baseline) |>
  filter(!is.na(accuracy), !is.na(bc_accuracy))

ggplot(am, 
       aes(x = accuracy)) +
  geom_histogram()

ggplot(am, 
       aes(x = bc_accuracy)) +
  geom_histogram()
```

Now check ICCs.

```{r}
# disaggregated
get_icc(am, column = "accuracy", object = "stimulus")
get_icc(am, column = "accuracy", object = "administration")
get_icc(am, column = "bc_accuracy", object = "stimulus")
get_icc(am, column = "bc_accuracy", object = "administration")
```

OK, so for this dataset it seems like within-trial baseline correction is **reducing** reliability for both stimuli and administrations. AM2018 still has relatively high reliability (in contrast to others). Let's try the SA dataset we were looking at before. 

```{r}
sa <- d_trial |>
  filter(dataset_name == "swingley_aslin_2002") |>
  group_by(trial_id, subject_id, administration_id, 
           target_label) |>
  summarise(baseline = mean(correct[t_norm < 500], na.rm=TRUE),
            accuracy = mean(correct[t_norm > 500], na.rm=TRUE), 
            bc_accuracy = accuracy - baseline) |>
  filter(!is.na(accuracy))

ggplot(am, 
       aes(x = accuracy)) +
  geom_histogram()

ggplot(am, 
       aes(x = bc_accuracy)) +
  geom_histogram()

# disaggregated
get_icc(sa, column = "accuracy", object = "stimulus")
get_icc(sa, column = "accuracy", object = "administration")
get_icc(sa, column = "bc_accuracy", object = "stimulus")
get_icc(sa, column = "bc_accuracy", object = "administration")
```

Weirdly it looks like the reverse is happening. Let's get more systematic. 

```{r}
d_summary <- d_trial |>
  group_by(dataset_name, trial_id, subject_id, administration_id, 
           target_label) |>
  summarise(baseline = mean(correct[t_norm < 500], na.rm=TRUE),
            accuracy = mean(correct[t_norm > 500], na.rm=TRUE), 
            bc_accuracy = accuracy - baseline, 
            target = sum(correct[t_norm > 500], na.rm=TRUE),
            target_baseline = sum(correct[t_norm < 500], na.rm=TRUE),
            distractor = sum(!correct[t_norm > 500], na.rm=TRUE), 
            distractor_baseline = sum(!correct[t_norm < 500], na.rm=TRUE), 
            elogit_baseline = log( (target_baseline + .5) / 
                                     (distractor_baseline + .5) ),
            elogit = log( (target + .5) / 
                            (distractor + .5) ), 
            elogit_bc = elogit - elogit_baseline) |>
  filter(!is.na(accuracy), !is.na(bc_accuracy), !is.na(elogit), !is.na(elogit_bc))

iccs <- d_summary |>
  group_by(dataset_name) |> 
  nest() |>
  mutate(icc_stimulus_acc = unlist(map(data, ~get_icc(.x, 
                                                      column = "accuracy",
                                                      object = "stimulus"))),
         icc_admin_acc = unlist(map(data, ~get_icc(.x, 
                                                   column = "accuracy",
                                                   object = "administration"))),
         icc_stimulus_bc = unlist(map(data, ~get_icc(.x, 
                                                     column = "bc_accuracy",
                                                     object = "stimulus"))),
         icc_admin_bc = unlist(map(data, ~get_icc(.x, 
                                                  column = "bc_accuracy",
                                                  object = "administration"))),
         icc_stimulus_elogit = unlist(map(data, ~get_icc(.x, 
                                                         column = "elogit",
                                                         object = "stimulus"))),
         icc_admin__elogit = unlist(map(data, ~get_icc(.x, 
                                                       column = "elogit",
                                                       object = "administration"))),
         icc_stimulus_elogitbc = unlist(map(data, ~get_icc(.x, 
                                                           column = "elogit_bc",
                                                           object = "stimulus"))),
         icc_admin_elogitbc = unlist(map(data, ~get_icc(.x, 
                                                        column = "elogit_bc",
                                                        object = "administration")))) |>
  select(-data) |>
  unnest(cols = c())
```

Let's plot these. 

```{r}
iccs_long <- iccs |>
  pivot_longer(-dataset_name, names_to = "measure", values_to = "icc") |>
  separate(measure, into = c("extra", "dimension","measure")) |>
  select(-extra) 

ggplot(iccs_long, 
       aes(x = measure, y = icc, group = dataset_name)) + 
  geom_point() +
  geom_line(alpha = .5) + 
  stat_summary(aes(group = 1), col = "red") + 
  facet_wrap(~dimension) +
  ylim(0,1) + 
  ylab("ICC") + 
  xlab("Measure")
```

