---
title: "Order effects"
author: "Hackathon"
date: "2024-08-27"
output: 
  html_document:
    toc: true
---

Goal: understand order effects.

DVs:

* we primarily care about outcomes like RT and accuracy (as we are measuring), but also care about level of "has-rt" (since looking to target at t=0 will reduce that), and do care (some) about looks before and around t=0. 

for each comparison, I do

* time course graph on -500 to 2000
* 5 models -- -500-0 (if data on this range); 0-400; RT; accuracy on 500-4000; has-rt

IVs:

* trial order -- for stimuli seen for the first time how does position in order change?

* seen prev (as distractor) -- for stim how does 1st time compare to seen prev as distractor?
    * for models, also look at trial order x seen prev as distractor

* seen prev (as target) -- for stim how does 1st time compare to seen prev as target?
    * for models, also look at trial order x seen prev as target 

* for datasets where we have it -- 3 way on first; prev-dist; prev-target

# Prep
```{r, eval=T, echo=F}
knitr::opts_chunk$set(warning = F, message = F, echo = F, eval = F)
source(here::here("helper/common.R"))
source(here::here("helper/notebook_helper.R"))
d_aoi <- readRDS(here("cached_intermediates", "0_d_aoi.rds"))
library(lme4)
library(broom)
library(broom.mixed)
```

```{r, eval=T}
# set up dvs
window_0_400 <- d_aoi |>
  filter(t_norm >= 0, t_norm <= 400) |>
  group_by(trial_order, trial_id, administration_id, dataset_name, target_id, target_label, distractor_id, distractor_label) |>
  summarize(
    correct_late = mean(correct, na.rm = T),
    percent_existing = mean(!is.na(correct))
  ) |>
  filter(percent_existing >= .8) |>
  select(-percent_existing) |>
  filter(!is.na(correct_late)) |>
  ungroup() |>
  select(dataset_name, administration_id, trial_id, correct_late)

window_500_0 <- d_aoi |>
  group_by(trial_id, trial_order, administration_id, age, dataset_name, target_id, target_label, distractor_id, distractor_label) |>
  filter(min(t_norm) <= -500) |>
  filter(t_norm >= -500, t_norm < 0) |>
  group_by(trial_id, trial_order, administration_id, dataset_name, target_id, target_label, distractor_id, distractor_label) |>
  summarize(
    correct_early = mean(correct, na.rm = T),
    percent_existing = mean(!is.na(correct))
  ) |>
  filter(percent_existing >= .8) |>
  select(-percent_existing) |>
  filter(!is.na(correct_early)) |>
  ungroup() |>
  select(dataset_name, trial_id, administration_id, correct_early)

rts <- readRDS(here("cached_intermediates", "3_rts.rds")) |>
  filter(shift_type == "D-T") |>
  filter(window == 400, time_0, time_end, frac == 1) |>
  mutate(log_rt = log(rt)) |>
  ungroup() |>
  select(dataset_name, administration_id, trial_id, log_rt)

accuracy <- d_aoi |>
  filter(t_norm >= 400, t_norm <= 3000) |>
  group_by(dataset_name, trial_id, administration_id) |>
  summarize(accuracy = mean(correct, na.rm = T)) |>
  filter(!is.na(accuracy))

dvs <- window_0_400 |>
  full_join(window_500_0) |>
  full_join(rts) |>
  full_join(accuracy) |>
  mutate(has_rt = ifelse(is.na(log_rt), 0, 1))
```


```{r, eval=T}
# most datasets pair stims, but not all do, so need to figure out when seen
d_trial_summary_long <- d_aoi %>%
  ungroup() |>
  distinct(
    dataset_id, dataset_name, administration_id, trial_id, trial_order,
    target_id, distractor_id
  ) %>%
  pivot_longer(c("target_id", "distractor_id"), names_to = "type_of_stim", values_to = "stim_id") |>
  group_by(dataset_id, dataset_name, administration_id, stim_id) |>
  arrange(trial_order) |>
  mutate(
    target_image_appearance_num = row_number(),
    target_prior_role = case_when(
      lag(type_of_stim) == "target_id" ~ "target",
      lag(type_of_stim) == "distractor_id" ~ "distractor",
      T ~ NA
    )
  ) |>
  filter(type_of_stim == "target_id") |>
  select(dataset_name, administration_id, trial_id, target_id = stim_id, target_image_appearance_num, target_prior_role)

d_trial_summary <- d_aoi %>%
  ungroup() |>
  distinct(
    dataset_id, dataset_name, administration_id, trial_id, trial_order,
    target_id, target_label, distractor_label, distractor_id
  ) %>%
  # we put in stimulus pair alphabetically because it needs to be in a consistent order
  # so that we can group by the pairing and not by pairing x target
  rowwise() |>
  mutate(label_pair = paste(sort(c(target_label, distractor_label)), collapse = "_")) %>%
  mutate(stimulus_pair = paste(sort(c(target_id, distractor_id)), collapse = "_")) %>%
  # mutate(first_stimulus = sort(c(target_label, distractor_label))[1]) %>%
  arrange(dataset_id, administration_id, trial_order) %>%
  group_by(dataset_id, administration_id, stimulus_pair) %>%
  mutate(stimulus_pair_instance = seq(1, n())) %>% # stimulus_pair_instance is how many times you've seen this pair of stimuli
  group_by(dataset_id, administration_id, label_pair) %>%
  mutate(label_pair_instance = seq(1, n())) %>%
  group_by(dataset_id, administration_id, stimulus_pair, target_label) %>%
  mutate(stimulus_pair_target_instance = seq(1, n())) %>% # sttarget instance is how many times you've seen this pair of stimuli with this target as a target
  group_by(dataset_id, administration_id, label_pair, target_label) %>%
  mutate(label_pair_target_instance = seq(1, n())) %>% # sttarget instance is how many times you've seen this pair of stimuli with this target as a target
  group_by(dataset_name, stimulus_pair) |>
  mutate(max_stimulus_pair_instance = max(stimulus_pair_instance)) |>
  group_by(dataset_name, label_pair) |>
  mutate(max_label_pair_instance = max(label_pair_instance)) |>
  group_by(dataset_name, stimulus_pair, target_label) |>
  mutate(max_stimulus_pair_target_instance = max(stimulus_pair_target_instance)) |>
  ungroup() |>
  left_join(d_trial_summary_long)
```

# Models 
## Trial order


```{r, eval=T}
trial_order <- d_trial_summary |> filter(target_image_appearance_num == 1)

trial_order_mod <- trial_order |> left_join(dvs)

trial_order_results <- expand_grid(model = "trial_order", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~ trial_order + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = trial_order_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)
```



## Seen prev as distractor

note that we subset here to where the target is only the distractor for its partner
```{r, eval=T}
prev_dist <- d_trial_summary |>
  filter(target_image_appearance_num %in% c(1, 2)) |>
  filter(is.na(target_prior_role) | target_prior_role == "distractor") |>
  mutate(type = case_when(
    is.na(target_prior_role) ~ "first",
    T ~ "prev_as_distractor"
  )) |>
  filter(!(stimulus_pair_instance == 1 & type == "prev_as_distractor"))
```

```{r, eval=T}
prev_dist_mod <- prev_dist |> left_join(dvs)

prev_dist_results <- expand_grid(model = "prev_dist", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~ type + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = prev_dist_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)

prev_dist_results_interaction <- expand_grid(model = "prev_dist_interact", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~type*trial_order + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = prev_dist_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)
```

## Seen prev as target

```{r, eval=T}
prev_target <- d_trial_summary |>
  filter(target_image_appearance_num %in% c(1, 2)) |>
  filter(is.na(target_prior_role) | target_prior_role == "target") |>
  mutate(type = case_when(
    is.na(target_prior_role) ~ "first",
    T ~ "prev_as_target"
  )) |>
  filter(!(stimulus_pair_instance == 1 & type == "prev_as_target"))
```

```{r, eval=T}
prev_target_mod <- prev_target |> left_join(dvs)

prev_target_results <- expand_grid(model = "prev_target", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~ type + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = prev_target_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)

prev_target_results_interaction <- expand_grid(model = "prev_target_interact", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~type*trial_order + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = prev_target_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)
```

## compare all three

```{r, eval=T}
prev_any <- d_trial_summary |>
  filter(target_image_appearance_num %in% c(1, 2)) |>
  mutate(type = case_when(
    is.na(target_prior_role) ~ "first",
    target_prior_role == "target" ~ "prev_as_target",
    target_prior_role == "distractor" ~ "prev_as_distractor"
  )) |>
  filter(type == "first" | stimulus_pair_instance == 2)
```

```{r, eval=T}
prev_any_mod <- prev_any |> left_join(dvs)

prev_any_results <- expand_grid(model = "prev_any", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~ type + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = prev_any_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)

prev_any_results_interaction <- expand_grid(model = "prev_any_interact", dv = c("correct_early", "correct_late", "accuracy", "has_rt", "log_rt")) |>
  mutate(results = map(dv, \(dv){
    lmer(str_c(dv, "~type*trial_order + (1|administration_id)+(1|target_label)+(1|dataset_name)"), data = prev_any_mod) |> tidy(conf.int = T)
  })) |>
  unnest(results)
```
```{r}
bind_rows(trial_order_results, prev_dist_results, prev_dist_results_interaction, prev_target_results, prev_target_results_interaction, prev_any_results, prev_any_results_interaction) |> saveRDS(here("cached_intermediates/7_model_summary.rds"))
```
# Viz

```{r}
results_summ <- readRDS(here("cached_intermediates/7_model_summary.rds"))
```

```{r}
results_summ |>
  filter(effect == "fixed", term != "(Intercept)") |>
  mutate(
    clean_type = case_when(
      term == "trial_order" ~ "trial order",
      term == "typeprev_as_target" ~ "prev target",
      term == "typeprev_as_distractor" ~ "prev distractor",
      term == "typeprev_as_target:trial_order" ~ "prev target : trial order",
      term == "typeprev_as_distractor:trial_order" ~ "prev distractor : trial order",
      T ~ term
    )
  ) |>
  ggplot(aes(dv, y = estimate, ymin = conf.low, ymax = conf.high, color = model, group = interaction(model, dv, term))) +
  geom_hline(yintercept=0)+
  geom_pointrange(position = position_dodge(width = .5)) +
  facet_wrap(~clean_type, scales = "free_x") +
  coord_flip()+theme(legend.position = "bottom")
```

The effects of having a target image that has been seen 1 time previously (as distractor or target), versus a target image that is being seen for the first time are (if they exist) have central estimates around 1% of the time more or less looking (both for windows around 0 and actual accuracy). These effects may well interact with trial order, although again, effects and interactions, if they exist, are small.  
Log RT has a larger scale than the other measures that are all on 0-1. Looks like there's something where prev target's looking time changes over trial num in a weird way. If anything, more looking to previous distractors on the accuracy window. 

At least across datasets, we cannot detect reliable effects of previously seen items or trial order on any of the DVs. 
