---
title: "Order effects"
author: "Hackathon"
date: "2024-08-27"
output: html_document
---

Goal: understand order effects.

```{r}

source(here::here("helper/common.R"))

```

# 1. Data preparation

## 1.1. Data summary

Create d_trial_summary dataframe which contains pre_accuracy and post_accuracy grouped by: dataset_id, dataset_name, administration_id, trial_id, trial_order, age, target_id, target_label, distractor_label.

```{r}

d_trial_summary <- d_trial %>%
  
  group_by(dataset_id, dataset_name, administration_id, trial_id, trial_order, 
           age, target_id, target_label, distractor_label) %>%
  summarise(pre_accuracy = mean(correct[t_norm <= 200], na.rm = TRUE),
            post_accuracy = mean(correct[t_norm > 200], na.rm = TRUE)) |>
  filter(!is.na(post_accuracy))

```

We also create some new columns: 

-   stimulus_pair: groups stimulus by their paired appearance irrespective of which one appeared as target.

-   first_stimulus: Tells which of the stimulus appeared first as target. The procedude could be improved because it differentiates stimulus by ordering them alphabetically.

-   stimulus_pair_instance: tells the time of appearance of each stimulus_pair

-   is_first_stimulus: is a boolean tells if the stimulus is the 1st or 2nd to appear as a target

-   stimulus_pair_target_instance: tells the time of appearance of each pair with a specific stimulus as target.
-   max_stimulus_pair_instance: tells the maximum number of trials repetitions in the dataset

## 1.2. New columns

```{r}

d_trial_summary <- d_trial_summary %>%
  # we put in stimulus pair alphabetically because it needs to be in a consistent order
  # so that we can group by the pairing and not by pairing x target
  mutate(stimulus_pair = paste(sort(c(target_label, distractor_label)), collapse = "_"),
                  first_stimulus = sort(c(target_label, distractor_label))[1]) %>% 
  arrange(dataset_id, administration_id, trial_order) %>%
  group_by(dataset_id, administration_id, stimulus_pair) %>%
  mutate(stimulus_pair_instance = seq(1,n()), # instance is how many times you've seen this pair of stimuli
         is_first_stimulus = ifelse(target_label == first_stimulus, TRUE, FALSE)) %>% 
  ungroup() %>%
  group_by(dataset_id, administration_id, stimulus_pair, target_label) %>%
  mutate(stimulus_pair_target_instance = seq(1,n())) %>% # target instance is how many times you've seen this pair of stimuli with this target as a target
  ungroup() %>% 
  mutate(max_stimulus_pair_instance = max(stimulus_pair_instance), .by = "dataset_id")
  
```


# 2. Repetitions analysis

## 2.1. Repetitions classification

We could focus in trials with stimulus_pair_instance == 1 \| 2 to make it easier to approach. In that case, we should have these combinations

| Stimulus_pair_instance | Stimulus_target_instance |                                                              |
|------------------------|--------------------------|--------------------------------------------------------------|
| 1                      | 1                        | 1st time pair and target are shown                           |
| 2                      | 1                        | 1st time target was shown even though pair was already shown |
| 2                      | 2                        | 2nd time target is shown along with pair                     |

 
```{r}

repetitions_data = d_trial_summary %>% 
  filter(max_stimulus_pair_instance >= 2) %>%
  
  filter(stimulus_pair_instance <= 2) %>% 
  
  mutate(type_of_instance = as.factor(case_when(
    
    stimulus_pair_instance == 1 & stimulus_pair_target_instance == 1 ~ "Not repeated",
    stimulus_pair_instance == 2 & stimulus_pair_target_instance == 1 ~ "Repeated pair",
    stimulus_pair_instance == 2 & stimulus_pair_target_instance == 2 ~ "Repeated pair and target"
    
  ))) 


repetitions_data_long = repetitions_data%>% 
  # filter(type_of_instance != "Repeated pair and target") %>% 
  select(administration_id,age,dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance, post_accuracy, pre_accuracy) %>% 
  pivot_longer(-c(administration_id,age,dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance),
               values_to = "Accuracy",
               names_to = "Time") 

repetitions_data_long %>% 
  group_by(dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance, Time) %>% 
  summarize(n = n()) %>% 
  group_by(dataset_name) %>% 
  mutate(total_trials = sum(n),
         proportion = n/total_trials) %>% 

  ggplot(aes(x = dataset_name, y = proportion, fill = (type_of_instance)))+
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "top")+
  coord_flip()


```


We should decide what to do with datasets/trials with very few repeated pair and target

absence of green in pomper_prime is suspicious
Clarify that only 2 first trials were selected

Select two or three datasets and see if this makes sense


## 2.2. Accuracy by repetitions faceted by dataset_name

```{r, fig.width=10, fig.height=10, fig.fullwidth=TRUE}


repetitions_data_long%>% 
    group_by(dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance, Time) %>% 
  summarize(mean_accuracy = mean(Accuracy, na.rm = T),
            se_accuracy = sd(Accuracy, na.rm = T)/sqrt(length(Accuracy)),
            n = n()) %>% 

  ggplot(aes(x = type_of_instance,
             y = mean_accuracy, color = Time)) + 
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_accuracy-se_accuracy,
                    ymax = mean_accuracy+se_accuracy), width = 0.2, size = 1)+
  # geom_smooth(method = "lm")+
  facet_wrap(~dataset_name)+
  theme_minimal()+
  theme(legend.position = "bottom")


```
trial number by repeat type

number of types it's been a distractor vs a  number of times its been a target


## 2.3. Accuracy by repetitions in the whole dataset

Standard errors might be a bit underestimated because of the number of rows


```{r}

repetitions_data_long%>% 
  
  group_by(dataset_name, administration_id, type_of_instance, Time) %>% 
  summarize(mean_administration_accuracy = mean(Accuracy, na.rm = T),
            n = n()) %>%
  ungroup() %>% 
  mutate(n_in_dataset = n(), .by = c("dataset_name","type_of_instance", "Time")) %>% 
  filter(n_in_dataset > 10) %>% 
  group_by(type_of_instance, Time) %>% 
  summarise(mean_accuracy = mean(mean_administration_accuracy, na.rm = T),
            se_accuracy = sd(mean_administration_accuracy, na.rm = T)/sqrt(length(mean_administration_accuracy)),
            n = n()) %>% 
  

  ggplot(aes(x = type_of_instance,
             y = mean_accuracy, color = Time)) + 


  geom_errorbar(aes(ymin = mean_accuracy-se_accuracy,
                    ymax = mean_accuracy+se_accuracy), width = 0.3, size = 1) +
    geom_point(aes(fill = Time),size = 5, color = "black", shape = 21) +
      coord_cartesian(ylim = c(0.2,0.8))+

  theme_minimal()



```
## 2.4. Accuracy by repetitions in the whole dataset

Same plot that before, but with lines showing accuracy in different datasets

```{r}

averaged_repetitions_data = repetitions_data_long %>% 
  
 
  filter(!is.na(Accuracy)) %>% 
  group_by(type_of_instance, Time) %>% 
  mutate(total_mean_accuracy = mean(Accuracy),
         total_se_accuracy = sd(Accuracy)/sqrt(length(Accuracy))) 



repetitions_data_long%>% 

  group_by(dataset_name, administration_id, type_of_instance, Time) %>% 
  summarize(mean_administration_accuracy = mean(Accuracy, na.rm = T),
            n = n()) %>% 
    ungroup() %>% 
  mutate(n_in_dataset = n(), .by = c("dataset_name","type_of_instance", "Time")) %>% 
  filter(n_in_dataset > 10) %>% 
  group_by(dataset_name, type_of_instance, Time) %>% 
  summarise(mean_accuracy = mean(mean_administration_accuracy, na.rm = T),
            se_accuracy = sd(mean_administration_accuracy, na.rm = T)/sqrt(length(mean_administration_accuracy)),
            n = n()) %>% 
  left_join(averaged_repetitions_data) %>% 


  

  ggplot(aes(x = type_of_instance)) + 
  
  geom_ribbon(aes(ymin = mean_accuracy - se_accuracy, ymax = mean_accuracy + se_accuracy, 
                  group = interaction(dataset_name, Time), fill = Time),
              alpha = 0.09) +
  geom_errorbar(aes(ymin = total_mean_accuracy-total_se_accuracy,
                    ymax = total_mean_accuracy+total_se_accuracy), width = 0.25, size = 1)+
  geom_point(aes(y = total_mean_accuracy, fill = Time),size = 5, color = "black", shape = 21) +

  # geom_line(aes(y = mean_accuracy,  group = interaction(dataset_name, Time),color = Time), size = 2, alpha = 0.1)+
  coord_cartesian(ylim = c(0.2,0.8))+
  theme_minimal()




```
## 2.5. Accuracy by repetitions and age

Same plot that before, but looking at age differences in children between 12 and 24 months


```{r}

# ADD AGE.

repetitions_data_long%>% 
    ungroup() %>% 
  mutate(n_in_dataset = n(), .by = c("dataset_name","type_of_instance", "Time")) %>%
  filter(n_in_dataset > 10) %>%
  filter(age >= 12) %>%  
  filter(age <= 24) %>% 
  mutate(age_bin = factor(cut(age, breaks = 3))) %>% 
  mutate(Time = factor(Time, levels = c("pre_accuracy", "post_accuracy"))) %>% 
  

  group_by(administration_id, type_of_instance, Time, age_bin) %>% 
  summarize(mean_administration_accuracy = mean(Accuracy, na.rm = T),
            n = n()) %>% 
  group_by(type_of_instance, Time, age_bin) %>% 
  summarise(mean_accuracy = mean(mean_administration_accuracy, na.rm = T),
            se_accuracy = sd(mean_administration_accuracy, na.rm = T)/sqrt(length(mean_administration_accuracy)),
            n = n()) %>% 
  

  ggplot(aes(x = factor(age_bin),
             y = mean_accuracy, color = type_of_instance )) + 


  geom_errorbar(aes(ymin = mean_accuracy-se_accuracy,
                    ymax = mean_accuracy+se_accuracy), width = 0.3, size = 1) +
    geom_point(aes(fill = type_of_instance),size = 5, color = "black", shape = 21) +
      # coord_cartesian(ylim = c(0.4,0.66))+

  theme_minimal()+
  theme(legend.position = "bottom")+
  facet_wrap(~Time)




  

```

# 3. Timecourse plots

## 3.1. Timecourse by type of instance

```{r, fig.width= 6, fig.height= 6}

rep_timecourse <- d_trial %>%
  left_join(repetitions_data) %>% 
  filter(!is.na(type_of_instance))



# do you look more to target after having seen this target as a target in this stimulus pair before?
rep_timecourse %>%
  group_by(type_of_instance, t_norm) %>%
  summarize(accuracy = mean(correct, na.rm=TRUE)) %>%
  filter(t_norm > -3000, t_norm < 4000) %>%
  ggplot(aes(x = t_norm, y = accuracy, color = type_of_instance)) + 
  geom_smooth(method="gam")+
  geom_vline(xintercept=0)+
  geom_hline(yintercept=0.5,linetype="dashed")+
  theme_minimal()+
  theme(legend.position = "bottom")


```

The "dip" seems to be happening only in trials in which the pair was repeated but with switched target. Children may be anticipating where to look. 

On the other hand, when the repeated trial involves repeating the target, this involves better accuracy both in the pre and post. In post, both types of repetitions elicit better accuracy levels than no-repetitions. When the pair and target are repeated, the accuracy peak is reached faster.


## 3.2. timecourse by type of instance and age


```{r}

filt_rep_data = repetitions_data  %>% 
  mutate(n_in_dataset = n(), .by = c("dataset_name","type_of_instance")) %>%
  filter(n_in_dataset > 10)


rep_timecourse <- d_trial %>%
  left_join(filt_rep_data) %>% 
  
  filter(!is.na(type_of_instance)) %>% 
  filter(age >= 14) %>%  
  filter(age <= 18) %>% 
  mutate(age_bin = cut(age, breaks = 3)) 
  


# do you look more to target after having seen this target as a target in this stimulus pair before?
rep_timecourse %>%
  group_by(type_of_instance, t_norm, age_bin) %>%
  summarize(accuracy = mean(correct, na.rm=TRUE)) %>% 
  filter(t_norm > -3000, t_norm < 4000) %>%
  ggplot(aes(x = t_norm, y = accuracy, color = as.factor(type_of_instance))) + 
  geom_smooth(method="gam")+
  # geom_point()+
  geom_vline(xintercept=0)+
  geom_hline(yintercept=0.5,linetype="dashed")+
  theme_minimal()+
  facet_wrap(~age_bin)


```


```{r}
options(scipen = 999)

rep_timecourse %>% 
  ggplot(aes(x = age, fill = type_of_instance))+
  geom_histogram()



```

# 4. Stuff for further exploration

We could focus in trials with stimulus_pair_instance == 1 \| 2 to make it easier to approach. In that case, we should have these combinations

| Stimulus_pair_instance | Stimulus_target_instance |                                                              |
|------------------------|--------------------------|--------------------------------------------------------------|
| 1                      | 1                        | 1st time pair and target are shown                           |
| 2                      | 1                        | 1st time target was shown even though pair was already shown |
| 2                      | 2                        | 2nd time target is shown along with pair                     |
| 3                      | 1                        | 1st time target is shown (was distractor 2 times before)
  3                        2                          2st time target is show (was distractor 1 times before)
  3                        3                          3rd time target is show (never was distractor before)
 


```{r}


repetitions_data = d_trial_summary %>% 
  filter(max_stimulus_pair_instance >= 3) %>%
  
  filter(stimulus_pair_instance <= 3) %>% 
  
  mutate(type_of_instance = case_when(
    
    stimulus_pair_instance == 1 & stimulus_pair_target_instance == 1 ~ "0 tgt | 0 dist",
    stimulus_pair_instance == 2 & stimulus_pair_target_instance == 1 ~ "0 tgt | 1 dist",
    stimulus_pair_instance == 2 & stimulus_pair_target_instance == 2 ~ "1 tgt | 0 dist",
    stimulus_pair_instance == 3 & stimulus_pair_target_instance == 1 ~ "0 tgt | 2 dist",
    stimulus_pair_instance == 3 & stimulus_pair_target_instance == 2 ~ "1 tgt | 1 dist",
    stimulus_pair_instance == 3 & stimulus_pair_target_instance == 3 ~ "2 tgt | 0 dist",
  )) %>% 
  mutate(type_of_instance = factor(type_of_instance, levels = c("0 tgt | 0 dist", "1 tgt | 1 dist", "0 tgt | 2 dist", "2 tgt | 0 dist", "0 tgt | 1 dist", "1 tgt | 0 dist")))


repetitions_data_long = repetitions_data%>% 
  # filter(type_of_instance != "Repeated pair and target") %>% 
  select(dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance, post_accuracy, pre_accuracy) %>% 
  pivot_longer(-c(dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance),
               values_to = "Accuracy",
               names_to = "Time") 

repetitions_data_long %>% 
  group_by(dataset_name, stimulus_pair_instance ,stimulus_pair_target_instance, type_of_instance, Time) %>% 
  summarize(n = n()) %>% 
  group_by(dataset_name) %>% 
  mutate(total_trials = sum(n)) %>% 

  ggplot(aes(x = dataset_name, y = n/total_trials, fill = (type_of_instance)))+
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "top")+
  coord_flip()

c







```







# 5. Prior materials

```{r}

rep_timecourse %>% group_by(dataset_name, stimulus_pair_instance, trial_id) %>% summarize(n = n()) %>% group_by(dataset_name, stimulus_pair_instance) %>% summarise(n = n())

```

```{r boxplot}

d_trial_summary %>% 
  group_by(dataset_name, stimulus_pair, stimulus_pair_instance,stimulus_pair_target_instance, is_first_stimulus) %>% 
  summarise(avg = mean(post_accuracy),
            n())
  


```



```{r}

# number of kids per instance by dataset will help us find datasets that have
# repetition by-design vs by-chance or error
kids_per_instance_table = d_trial_summary %>%
  

  distinct(dataset_name, stimulus_pair_instance, administration_id) %>% 
  

  group_by(dataset_name, stimulus_pair_instance) %>% 
  summarise(n = n()) %>% 
  group_by(dataset_name) %>% 
  mutate(total = sum(n)) %>% 
  ungroup()

# Stacked barplot with proportions

kids_per_instance_table %>% 

  ggplot(aes(x = dataset_name, y = n/total, fill = (stimulus_pair_instance)))+
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "top")+
  coord_flip()


# filtered stacked barplot with proportions

kids_per_instance_table %>% 
    mutate(max_instances = max(stimulus_pair_instance),.by = c("dataset_name")) %>% 
  filter( max_instances > 2) %>% 
  filter( max_instances <5) %>% 
    filter(dataset_name != "baumgartner_2014") %>% 
  filter(dataset_name != "swingley_aslin_2002") %>% 
  ggplot(aes(x = dataset_name, y = n/total, fill = (stimulus_pair_instance)))+
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "top")+
  coord_flip()




d_trial_summary %>% group_by(dataset_name) %>% 
  summarize(n_kids = n_distinct(administration_id))
  

```


```{r}



# Keep only "valid" datasets

rep_valid = d_trial_summary 
  # filter(dataset_name != "baumgartner_2014") %>% 
  # filter(dataset_name != "swingley_aslin_2002")

# get trials that have more than one instance and less than 5
rep_trials <- d_trial_summary %>%
  group_by(dataset_id, administration_id, stimulus_pair) %>%
  mutate(max_instances = max(stimulus_pair_instance)) %>% 
  ungroup() %>%
  filter(max_instances > 2) %>% 
  filter(max_instances < 5)

# get datasets with repeated trials
rep_datasets <- rep_trials %>%
  distinct(dataset_id)

# just the second time seeing this stimulus pair
rep_timecourse <- d_trial %>%
  left_join(rep_trials) %>% 
  filter(max_instances > 1)




# do you look more to target after having seen this target as a target in this stimulus pair before?
rep_timecourse %>%
  group_by(stimulus_pair_instance, t_norm) %>%
  summarize(accuracy = mean(correct, na.rm=TRUE)) %>%
  filter(t_norm > -3000, t_norm < 4000) %>%
  ggplot(aes(x = t_norm, y = accuracy, color = as.factor(stimulus_pair_instance))) + 
  geom_smooth(method="gam")+
  geom_vline(xintercept=0)+
  geom_hline(yintercept=0.5,linetype="dashed")# +
  #facet_wrap(~stimulus_pair_instance)

# The same as the previous, faceted by study

rep_timecourse %>%
  group_by(stimulus_pair_instance, t_norm,dataset_name) %>%
  summarize(accuracy = mean(correct, na.rm=TRUE)) %>%
  filter(t_norm > -3000, t_norm < 4000) %>%
  ggplot(aes(x = t_norm, y = accuracy, color = as.factor(stimulus_pair_instance))) + 
  geom_smooth(method="gam")+
  geom_vline(xintercept=0)+
  geom_hline(yintercept=0.5,linetype="dashed")+
  facet_wrap(~dataset_name)+
  theme(legend.position = "bottom")



# do you look more to target after having seen this target as a target in this stimulus pair before? faceted by age
# rep_timecourse %>%
#   mutate(age_bin = cut(age, breaks = 4)) %>%
#   group_by(age_bin, stimulus_pair_instance, t_norm) %>%
#   summarize(accuracy = mean(correct, na.rm=TRUE)) %>%
#   filter(t_norm > -2000, t_norm < 4000) %>%
#   ggplot(aes(x = t_norm, y = accuracy, color = as.factor(stimulus_pair_instance)), group = age_bin) + 
#   geom_smooth(method="gam")+
#   facet_wrap(~age_bin) +
#   geom_vline(xintercept=0)+
#   geom_hline(yintercept=0.5,linetype="dashed")

# get all the repeated stimulus pairs (up to 5 repeats)
# rep_timecourse <- d_trial %>%
#   filter(trial_id %in% rep_trials$trial_id) %>%
#   left_join(rep_trials) %>%
#   filter(instance < 5, max_instances > 1)
  
# how does looking change depending on # times you've seen this target as a target in this stim pair?
# rep_timecourse %>%
#   group_by(instance, target_instance, t_norm) %>%
#   summarize(accuracy = mean(correct, na.rm=TRUE), weight = n()) %>% 
#   ungroup() %>%
#   filter(weight > 100) %>%
#   filter(t_norm > -2000, t_norm < 4000) %>%
#   ggplot(aes(x = t_norm, y = accuracy, color = as.factor(target_instance))) + 
#   geom_point(aes(size = log(weight)), shape = 21, alpha = 0.4, fill = NA) +
#   geom_smooth(method="gam", aes(weight = weight, fill = as.factor(target_instance))) +
#   facet_wrap(~instance) +
#   geom_vline(xintercept=0)+
#   geom_hline(yintercept=0.5,linetype="dashed") +
#   theme_bw()

```

```{r}
d_repeated_datasets <- d_trial_summary %>% 


d_trial_summary %>% 
  group_by(stimulus_pair_instance, dataset_name) %>% 
  summarize(mean_accuracy = mean(post_accuracy, na.rm = T)) %>% 
  ggplot(aes(x = stimulus_pair_instance, y = mean_accuracy)) +
  geom_point() +
  facet_wrap(~dataset_name) +
  theme_minimal()
```
