---
title             : "Peekbank Methods"
shorttitle        : "Peekbank"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Enter author note here.

abstract: |
  Lorem ipsum sit dolor hic sunt leones. 
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction


Early language is important construct for science, clinical applications, etc. 
The looking while listening task is a good measure of early language processing. 
- task description
- real time measure, not just knowledge 
- could be a sensitive measure, could be something different. we're not going to talk about what construct it taps. 

LWL is used for individual differences and predicting later success, as well as widely used in experimental studies investigating priming, semantic similarity, generalization etc. etc. 

Reliability and validity of the measure is important. reliability prerequisite. But many early childhood measures have low reliability. 
- byers-heinlein six solutions
- measurement schmeasurement
- MB test-retest

ICC as one approach to measure reliability. 

[setup importance of word recognition/ LWL in particular - 1 or 2 paragraphs]

[define problem: how do we establish data analysis strategies that help us understand what we care about. Can we do this in a data-driven way]

goals:
- make data-driven recommendations based on Peekbank for data analysis strategies that maximize reliability
(- and validity? Would require incorporating some independent data/ trying to configure CDI pipeline)

People do lots of things when they analyze LWL data. 
- accuracy (average accuracy within a fixed window)
- baseline-corrected accuracy (average accuracy subtracting an average baseline)
also they compute reaction time (ms) - Fernald et al. (2008)

In this context, what is the best practice for maximizing reliability in LWL? 
- What window should you use?
- How to decide when to include trials and participants
- whether to do baseline corrections
- how to compute the most reliable reaction times
- how to get the most stable estimates of accuracy and reaction time for individuals

No one dataset can address these questions, and there is often some circularity - you can't make these decisions on the same dataset you then analyze in your paper. So using independent data is critical.   
We can answer these questions using a new dataset: Peekbank. allows empirical measurement of the consequences of analytic decisions for reliability. 

Contributions
- make data-driven recommendations based on Peekbank for data analysis strategies that maximize reliability
(- and validity? Would require incorporating some independent data/ trying to configure CDI pipeline)


# Dataset and appraoch

Subset of peekbank that we are using

Descriptives on datasets/number of trials

Illustrate the ICC approach to reliability 

# Results

Recommendation 1: To maximize reliability, choose long time windows.

- time window within dataset
- test retest 

- make sure that in phonetic competition you still see the same thing - check on the competition in swingley and aslin - do longer windows show bigger condition effects?

[WHAT ABOUT BASELINE CORRECTION]


Recommendation 2: RT guidance
- Reliability
- Windowing

- what counts as a t start vs d. start (ELIKA) - how many D fixations etc. 


Recommendation 3: [recommendation about how to set missingness criteria & how to deal with zoners - probably err on the side of including more data?]
- how many trials?
- how much data per trial?
- zoning trials + zoning trials


Recommendation 4: Number of trials for stable individual kid measures or for condition differences
- stable overall kid values
- item-level effects
- within-participant designs/ detecting a condition difference

Not just ICC for subjects or items, but also our power to recover condition effects. 

- use totlot or others to simulate effects of n-trials



# Discussion

- Validity questions - recommendations towards what we should do as a field to validate these measures


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
