---
title             : "Peekbank Methods"
shorttitle        : "Peekbank"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

goals:
- make data-driven recommendations based on Peekbank for data analysis strategies that maximize reliability
(- and validity? Would require incorporating some independent data/ trying to configure CDI pipeline)

We consider three commonly used dependent variables:
- accuracy (average accuracy within a fixed window)
- baseline-corrected accuracy (average accuracy subtracting an average baseline)
- reaction time (ms)

Core question is how to make decisions within the processing pipeline that maximize key measure characteristics for these commonly used dependent variables.
- exclusions
-- missing data on a trial level
-- missing data on a participant level
-- other exclusion criteria
- window size
- how to handle "sticky" trials/ zoners

Setup each recommendation:
- 






# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

Recommendation 1: To maximize reliability, choose long time windows.

Recommendation 2: [recommendation about how to set missingness criteria & how to deal with zoners - probably err on the side of including more data?]
- how many trials?
- how much data per trial?
- zoning trials + zoning trials

Recommendation 3: RT guidance
- Reliability
- Windowing

Recommendation 4: Number of trials for stable individual kid measures and depending on research question- honing in on the individual differences question
- stable overall kid values
- within-participant designs/ detecting a condition difference
- item-level effects

# Discussion

- Validity questions - recommendations towards what we should do as a field to validate these measures


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
