---
title             : "Maximizing reliability and validity in measuring infant word recognition: Insights from the Peekbank dataset"
shorttitle        : "Peekbank"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "More authors"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Stanford University"
  - id            : "2"
    institution   : "UC San Diego"

authornote: |
  Enter author note here.

abstract: |
  Lorem ipsum sit dolor hic sunt leones. 
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["peekbank-methods-ref.bib"]

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{threeparttablex}
  - \usepackage{booktabs}
  - \usepackage{placeins}
  - \usepackage{float}
  - \renewcommand{\textfraction}{0.00}
  - \renewcommand{\topfraction}{1}
  - \renewcommand{\bottomfraction}{1}
  - \renewcommand{\floatpagefraction}{1}
  - \setcounter{topnumber}{5}
  - \setcounter{bottomnumber}{5}
  - \setcounter{totalnumber}{6} 
  - \renewcommand{\arraystretch}{0.75} 
  - \usepackage{setspace}
  - \singlespacing
---
<!-- (title ideas) -->


<!-- Using a large-scale database to establish data-driven guidance… -->
<!-- ... to evaluate measurement properties… -->
<!-- Data-driven guidance for infant looking-while-listening methods -->
<!-- Data-driven guidance for processing LWL data to maximize reliability and validity -->
<!-- Data-driven guidance for extracting the most reliability and validity from LWL data  -->



# Introduction

```{r setup, include = FALSE}
library("papaja")
library("here")
library(kableExtra)
source(here("helper/common.R"))
source(here("helper/notebook_helper.R"))
source(here("helper/rt_helper.R"))
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache=F)
```


```{r, eval=F}
included <- readRDS(here("cached_intermediates/0_d_aoi.rds")) |>
  filter(!is.na(correct)) |>
  distinct(administration_id, dataset_id, trial_id, subject_id, age)

included |>
  left_join(readRDS(here("cached_intermediates/0_cdi_subjects.rds"))) |>
  saveRDS(here("cached_intermediates/paper_dataset_summary.rds"))
```

```{r}
dataset_summ <- readRDS(here("cached_intermediates/paper_dataset_summary.rds"))
```

```{r}
dataset_table <- dataset_summ |>
  group_by(dataset_name) |>
  summarize(
    admins = n_distinct(administration_id),
    subjects = n_distinct(subject_id),
    trials = n(),
    age_min = min(age),
    age_mean = mean(age),
    age_max = max(age),
    has_cdi = sum(!is.na(prod) | !is.na(comp)) > 0
  ) |>
  left_join(make_test_retest_pairs(dataset_summ) |> group_by(dataset_name) |> tally() |> mutate(trt = n > 0) |> select(-n)) |>
  ungroup() |>
  mutate(
    pct_trial = trials / sum(trials),
    pct_admins = admins / sum(admins),
    pct_subjects = subjects / sum(subjects)
  ) |>
  mutate(age = sprintf("%.0f [%.0f - %.0f]", age_mean, age_min, age_max)) |>
  select(-age_mean, -age_min, -age_max) |>
  mutate(
    CDI = ifelse(has_cdi, "x", ""),
    `Test-retest` = ifelse(!is.na(trt), "x", "")
  ) |>
  select(dataset_name, trials, admins, subjects, age, CDI, `Test-retest`, pct_trial)

clean_names <- tribble(
  ~dataset_name, ~`Dataset Name`, ~`Language`,
  "reflook_v4", "Yurovsky et al. (2017)", "English",
  "yurovsky_2017", "Yurovsky & Frank (2017)", "English",
  "weaver_zettersten_2024", "Weaver et al. (2024)", "English",
  "fernald_marchman_2012", "Fernald & Marchman (2012)", "English",
  "frank_tablet_2016", "Frank et al. (2016)", "English",
  "fmw_2013", "Fernald et al. (2013)", "English",
  "adams_marchman_2018", "Adams et al. (2018)", "English",
  "potter_canine", "Potter & Lew Williams (2023)", "English",
  "fernald_totlot", "Fernald et al. (2006)", "English",
  "pomper_prime", "Pomper & Saffran (2015)", "English",
  "pomper_saffran_2016", "Pomper & Saffran (2016)", "Egnlish",
  "swingley_aslin_2002", "Swingley & Aslin (2002)", "English",
  "pomper_salientme", "Pomper & Saffran (2019)", "English",
  "perry_cowpig", "Perry & Saffan (2017)", "English",
  "ronfard_2021", "Ronfard et al. (2022)", "English",
  "bacon_gendercues", "Bacon & Saffran (2022)", "English",
  "garrison_bergelson_2020", "Garrison et al. (2020)", "English",
  "pomper_yumme", "Pomper & Saffran (2018)", "English",
  "mahr_coartic", "Mahr et al. (2015)", "English",
  "potter_remix", "Potter et al. (2019)", "English",
  "reflook_socword", "Yurovsky et al. (2013)", "English",
  "yoon_simpimp_2015", "Yoon et al. (2015)", "English",
  "borovsky_2019", "Borovsky & Peters (2019)", "English",
  "pomper_dimy", "Pomper & Saffran (2017)", "English",
  "weaver_saffran_2026", "Weaver & Saffran (2026)", "English",
  "bergelson_swingley_2012", "Bergelson & Swingley (2012)", "English",
  "moore_bergelson_2022_verb", "Moore & Bergelson (2022)", "English",
  "hurtado_2008", "Hurtado et al. (2008)", "Spanish",
  "kartushina_2019", "Kartushina & Mayor (2019)", "Norwegian",
  "weisleder_stl", "Weisleder & Fernald (2013)", "Spanish",
  "sander-montant_2022", "Sander-Montant et al. (2023)", "English, French",
  "gazetriggered_2020", "Egger et al. (2020)", "Dutch",
  "xsectional_2007", "Hurtado et al. (2007)", "Spanish",
  "casillas_tseltal_2015", "Casillas et al. (2017)", "Tseltal",
  "kremin_2021", "Kremin et al. (2023)", "English, French, Spanish",
  "byers-heinlein_2017", "Byers-Heinlein et al. (2017)", "English, French",
)

global_summary <- dataset_summ |>
  ungroup() |>
  summarize(
    admins = n_distinct(administration_id),
    subjects = n_distinct(subject_id),
    trials = n(),
    age_min = min(age),
    age_mean = mean(age),
    age_max = max(age),
    has_cdi = n_distinct(dataset_name[!is.na(prod) | !is.na(comp)])
  ) |>
  bind_cols(make_test_retest_pairs(dataset_summ) |> group_by(dataset_name) |> tally() |> summarize(`Test-retest` = n() |> as.character())) |>
  ungroup() |>
  mutate(
    pct_trial = trials / sum(trials),
    pct_admins = admins / sum(admins),
    pct_subjects = subjects / sum(subjects)
  ) |>
  mutate(age = sprintf("%.0f [%.0f - %.0f]", age_mean, age_min, age_max)) |>
  select(-age_mean, -age_min, -age_max) |>
  mutate(
    CDI = as.character(has_cdi),
    dataset_name = "Total",
    `Dataset Name` = "Total",
    ` ` = " ",
    `Pct Trials` = "100%",
    `Language` = ""
  )


dataset_table |>
  left_join(clean_names) |>
  arrange(desc(pct_trial)) |>
  mutate(
    ` ` = row_number() |> as.character(),
    `Pct Trials` = sprintf("%.1f%%", pct_trial * 100)
  ) |>
  bind_rows(global_summary) |>
  select(` `, `Dataset Name`, `Pct Trials`, `Trials` = trials, `Admins` = admins, `Subjects` = subjects, `Age` = age, `CDI`, `Test-retest`, `Language`) |>
  kable(format = "latex", caption = "Descriptives of the included datasets. \\label{tab:descriptives}", align = "rlrrrrrrrrl", digits = 2, booktabs = T, linesep = "") |>
  kable_styling(latex_options = "scale_down") |>
  row_spec(36, hline_after = T)
```


# helpers

```{r}
library(lme4)
library(broom.mixed)
library(cowplot)
library(emmeans)
dataset_summ <- readRDS(here("cached_intermediates/paper_dataset_summary.rds"))

filter_icc <- function(data, col_est) {
  include <- data |>
    group_by(dataset_name, across(any_of("age_bin"))) |>
    summarize(
      pct_0 = sum(.data[[col_est]] == 0) / n()
    )

  data |> semi_join(include |> filter(pct_0 < .5))
}

do_lollipop_plot <- function(df, name, include_condition){
  df |> mutate(name=name) |> 
    {{include_condition}}() |> 
    filter(!is.na(combined)) |> 
  ggplot(aes(x=reorder(dataset_name, est), y=est))+geom_line() + geom_point(aes(color=combined))+coord_flip()+labs(x="dataset", y="Correlation")+scale_color_solarized(accent="red")+facet_wrap(~name, nrow=1)+theme(legend.position="none")
}



set_of_lollis <- function(icc, cdi, trt, include_func){
  a <- do_lollipop_plot(icc |> filter_icc("est"), "ICC reliability", {{include_func}})
  b <- do_lollipop_plot( cdi |> filter(!is.na(comp_est)) |> rename(est=comp_est), "CDI Comp", {{include_func}})
  c <- do_lollipop_plot( cdi |> filter(!is.na(prod_est)) |> rename(est=prod_est), "CDI Prod", {{include_func}})
  d <- do_lollipop_plot( trt |> filter(!is.na(est)), "Test retest", {{include_func}})
  
g <- ggplotGrob(a + theme(legend.position = "bottom"))
leg <- g$grobs[[which(g$layout$name == "guide-box-bottom")]]

plot_grid(plot_grid(a,d), plot_grid(b,c), leg, nrow=3, rel_heights=c(1,1,.1)) 
}
```


```{r}
do_model <- function(df, make_baseline, weight_df, form){
  data <- df |> filter(!is.na(est)) |> 
    left_join(weight_df) |> 
    mutate(across(!est & !n_admins, as.factor)) |> 
    {{make_baseline}}()
  
  mod <- lmer(str_c("est ~", form, "+ (1 | dataset_name)"), data=data, weights=n_admins)
  emm <- emmeans(mod, as.formula(str_c("~", form)))
  contrast(emm, method = "trt.vs.ctrl", ref = 1) |> tidy(conf.int=T) 

}



make_model_plot <- function(df, x, col=NULL, facet=NULL, fix_function, lab, breaks=c( -.1,  0, .1), limits=c(-.2, .2)){
  facet_quo <- rlang::enquo(facet)
  p <-  df |> {{fix_function}}() |> ggplot(aes(x={{x}}, col={{col}}, y=estimate, ymin=conf.low, ymax=conf.high))+geom_pointrange()+coord_flip()+labs(y=lab)+scale_y_continuous(breaks=breaks, limits=limits)+geom_hline(yintercept=0)
  
  if (!rlang::quo_is_null(facet_quo)) {
    p <- p + facet_wrap(vars(!!facet_quo))
  }
  
  p

}

make_model_grid_plot <- function(icc, cdi, trt, make_baseline, form, x, col=NULL, facet=NULL, fix_function, breaks=c( -.1,  0, .1), limits=c(-.2, .2)){
  icc_plot<- do_model(icc |> filter_icc("est"), {{make_baseline}}, 
                          dataset_summ |> group_by(dataset_name) |> summarize(n_admins=n_distinct(administration_id)), 
                          form) |> make_model_plot({{x}}, col={{col}}, facet={{facet}}, fix_function={{fix_function}},
                                                   lab="ICC reliability", breaks, limits)
    comp_plot<- do_model(cdi |> filter(!is.na(comp_est)) |> rename(est=comp_est), {{make_baseline}}, 
                          dataset_summ |> group_by(dataset_name) |> filter(!is.na(comp)) |> summarize(n_admins=n_distinct(administration_id)), 
                          form) |> make_model_plot({{x}}, col={{col}}, facet={{facet}}, fix_function={{fix_function}},
                                                   lab="CDI Comp", breaks, limits)
        prod_plot<- do_model(cdi |> filter(!is.na(prod_est)) |> rename(est=prod_est), {{make_baseline}}, 
                          dataset_summ |> group_by(dataset_name) |> filter(!is.na(prod))|> summarize(n_admins=n_distinct(administration_id)), 
                          form) |> make_model_plot({{x}}, col={{col}}, facet={{facet}}, fix_function={{fix_function}},
                                                   lab="CDI Prod", breaks=breaks, limits=limits)
            trt_plot<- do_model(trt |> filter(!is.na(est)), {{make_baseline}}, 
                          dataset_summ |> make_test_retest_pairs() |> group_by(dataset_name) |>
    summarize(n_admins = n_distinct(pair_number)), 
                          form) |> make_model_plot({{x}}, col={{col}}, facet={{facet}}, fix_function={{fix_function}},
                                                   lab="TRT", breaks=breaks, limits=limits)
            plot_grid(plot_grid(icc_plot,trt_plot), plot_grid(comp_plot,prod_plot), nrow=2,rel_heights=c(1,1)) 
            
}
```


```{r}

bin_ages <- function(d_aoi, min_per_bin = 5) {
  d_aoi |>
    distinct(administration_id, age, dataset_name, across(any_of(c("prod", "comp", "pair_number")))) |>
    mutate(age_bin = case_when(
      age < 18 ~ "<18",
      age < 24 ~ "18-24",
      age < 36 ~ "24-36",
      age >= 36 ~ ">=36"
    )) |>
    group_by(dataset_name, age_bin) |>
    mutate(count = n()) |>
    filter(count >= min_per_bin) |>
    ungroup()
}
do_model_age<- function(df, make_baseline, weight_df, form){
  weight_df
  
  data <- df |> filter(!is.na(est)) |> 
    left_join(weight_df) |> 
    mutate(across(!est & !n_admins, as.factor)) |> 
    {{make_baseline}}()
  
  data |> group_by(age_bin) |> nest() |> 
    mutate(result=map(data,
      possibly(
  function(d) {
mod <- lmer(str_c("est ~", form, "+ (1 | dataset_name)"), data=d, weights=n_admins)
  emm <- emmeans(mod, as.formula(str_c("~", form)))
  contrast(emm, method = "trt.vs.ctrl", ref = 1) |> tidy(conf.int=T)   },
  otherwise = NULL
))) |> 
    select(-data) |>
      filter(!map_lgl(result, is.null)) |>
unnest(result) |> View()

}



make_model_plot_age <- function(df, x, col=NULL, facet=NULL, fix_function, lab, breaks=c( -.1,  0, .1), limits=c(-.2, .2)){
  facet_quo <- rlang::enquo(facet)
  View(df)
  p <-  df |> {{fix_function}}() |> ggplot(aes(x={{x}}, col=age_bin, y=estimate, ymin=conf.low, ymax=conf.high))+geom_pointrange()+coord_flip()+labs(y=lab)+scale_y_continuous(breaks=breaks, limits=limits)+geom_hline(yintercept=0)
  
  if (!rlang::quo_is_null(facet_quo)) {
    p <- p + facet_wrap(vars(!!facet_quo))
  }
  
  p

}

make_model_grid_plot_age <- function(icc, cdi, trt, make_baseline, form, x, facet=NULL, fix_function, breaks=c( -.1,  0, .1), limits=c(-.2, .2)){
  icc_plot<- do_model_age(icc |> filter_icc("est"), {{make_baseline}}, 
                          dataset_summ |> bin_ages() |> group_by(dataset_name, age_bin) |> summarize(n_admins=n_distinct(administration_id)), 
                          form) |> make_model_plot_age({{x}},  facet={{facet}}, fix_function={{fix_function}},
                                                   lab="ICC reliability", breaks, limits)
    comp_plot<- do_model_age(cdi |> filter(!is.na(comp_est)) |> rename(est=comp_est), {{make_baseline}}, 
                          dataset_summ |> bin_ages() |> group_by(dataset_name, age_bin) |> filter(!is.na(comp)) |> summarize(n_admins=n_distinct(administration_id)), 
                          form) |> make_model_plot_age({{x}},  facet={{facet}}, fix_function={{fix_function}},
                                                   lab="CDI Comp", breaks, limits)
        prod_plot<- do_model_age(cdi |> filter(!is.na(prod_est)) |> rename(est=prod_est), {{make_baseline}}, 
                          dataset_summ |> bin_ages() |> group_by(dataset_name, age_bin) |> filter(!is.na(prod))|> summarize(n_admins=n_distinct(administration_id)), 
                          form) |> make_model_plot_age({{x}}, facet={{facet}}, fix_function={{fix_function}},
                                                   lab="CDI Prod", breaks=breaks, limits=limits)
            trt_plot<- do_model_age(trt |> filter(!is.na(est)), {{make_baseline}}, 
                          dataset_summ |>  make_test_retest_pairs() |> mutate(age=mean_age)|>bin_ages()|> group_by(dataset_name, age_bin) |>
    summarize(n_admins = n_distinct(pair_number)), 
                          form) |> make_model_plot_age({{x}}, facet={{facet}}, fix_function={{fix_function}},
                                                   lab="TRT", breaks=breaks, limits=limits)
            plot_grid(plot_grid(icc_plot,trt_plot), plot_grid(comp_plot,prod_plot), nrow=2,rel_heights=c(1,1)) 
            
}
```
# accuracy 
```{r acc-heat-map, fig.cap="A heat map showing the average ICC across datasets for different start and end points for the accuracy window. A region with the highest ICC (best reliability) is outlined.", fig.width=5, fig.height=3}
icc_noboot <- readRDS(here("cached_intermediates", "1_acc_icc_noboot.rds")) 

include <- icc_noboot |> group_by(dataset_name) |> 
    summarize(pct_0=sum(icc==0)/n()) |> filter(pct_0<.5)

icc_noboot_summary <- icc_noboot |>semi_join(include) |> 
  group_by(t_start, t_end) |>
  summarize(
    N = n(),
    mean_icc = mean(icc, na.rm = TRUE)
  ) |>
  mutate(window_size = t_end - t_start)


ggplot(icc_noboot_summary, aes(x = t_start, y = t_end, fill = mean_icc)) +
  geom_tile(color = "white") +
  scale_fill_viridis(name = "Mean ICC", option = "magma") +
  scale_x_continuous(breaks = c(-500, 0, 500, 1000, 1500)) +
  geom_rect(aes(xmin = 550, xmax = 850, ymin = 2750, ymax = 4050), linewidth = 1, color = "black", fill = alpha("grey", 0)) +
  xlab("Window Start Time (in ms)") +
  ylab("Window End Time (in ms)")
```


```{r, fig.height=7, fig.width=6}

acc_include <- function(df){
  df |> mutate(combined=case_when(
    t_start==400 & t_end==3000 ~ "400-3000",
    t_start==200 & t_end==2000 ~ "200-2000",
    T ~ NA
  ))
}

set_of_lollis( readRDS(here("cached_intermediates/1_acc_icc_boot.rds")),  readRDS(here("cached_intermediates/1_acc_cdi_boot.rds")),   readRDS(here("cached_intermediates/1_acc_test_retest_boot.rds")), acc_include)
```

```{r, fig.height=7, fig.width=8}

baseline_acc <- function(df){
  df |>  mutate(
    t_start = relevel(t_start, "400"),
    t_end= relevel(t_end, "3000")
  )
}

fix_acc_interact <- function(df){
  df |> separate(contrast, sep=" ", c("start", "end", NA, NA, NA)) |> 
  mutate(t_start=str_replace(start, "t_start", "") |> as.numeric(),
         t_end=str_replace(end, "t_end", "") |> as.numeric()) 
  
}
make_model_grid_plot(readRDS(here("cached_intermediates/1_acc_icc_boot.rds")),  readRDS(here("cached_intermediates/1_acc_cdi_boot.rds")),   readRDS(here("cached_intermediates/1_acc_test_retest_boot.rds")), baseline_acc, "t_start * t_end", x=t_start, facet=t_end, fix_function=fix_acc_interact)
                                                                                                                                                    
```


```{r, fig.height=7, fig.width=8}

baseline_acc <- function(df){
  df |>  mutate(
    t_start = relevel(t_start, "400"),
    t_end= relevel(t_end, "3000")
  )
}

fix_acc_interact <- function(df){
  View(df)
  df |> separate(contrast, sep=" ", c("start", "end", NA, NA, NA)) |> 
  mutate(t_start=str_replace(start, "t_start", "") |> as.numeric(),
         t_end=str_replace(end, "t_end", "") |> as.numeric()) 
  
}
make_model_grid_plot_age(readRDS(here("cached_intermediates/1_acc_icc_boot_byage.rds")),  readRDS(here("cached_intermediates/1_acc_cdi_boot_byage.rds")),   readRDS(here("cached_intermediates/1_acc_test_retest_boot_byage_split.rds")), baseline_acc, "t_start * t_end", x=t_start, facet=t_end, fix_function=fix_acc_interact)
                                                                                                                                                    
```

# bc 
```{r, fig.height=7, fig.width=6}

baseline_lengths <- readRDS(here("cached_intermediates", "2_baseline_lengths.rds"))
bc_icc <- readRDS(here("cached_intermediates", "2_bc_icc_boot.rds")) |>
  bind_rows(readRDS(here("cached_intermediates", "1_acc_icc_boot.rds")) |> filter(t_start == 400)) |>
  filter(t_end == 3000) |>
  semi_join(baseline_lengths) |>
    mutate(b_start = ifelse(is.na(b_start), "none", as.character(b_start)),
         b_end=ifelse(is.na(b_end), "none", as.character(b_end)))

bc_cdi <- readRDS(here("cached_intermediates", "2_bc_cdi_boot.rds")) |>
  bind_rows(readRDS(here("cached_intermediates", "1_acc_cdi_boot.rds")) |> filter(t_start == 400)) |>
  filter(t_end == 3000) |>
  semi_join(baseline_lengths) |>
   mutate(b_start = ifelse(is.na(b_start), "none", as.character(b_start)),
         b_end=ifelse(is.na(b_end), "none", as.character(b_end))) 

bc_test_retest <- readRDS(here("cached_intermediates", "2_bc_test_retest_boot.rds")) |>
  bind_rows(readRDS(here("cached_intermediates", "1_acc_test_retest_boot.rds")) |> filter(t_start == 400)) |>
  filter(t_end == 3000) |>
  semi_join(baseline_lengths) |>
  mutate(b_start = ifelse(is.na(b_start), "none", as.character(b_start)),
         b_end=ifelse(is.na(b_end), "none", as.character(b_end)))


bc_include <- function(df){
  df |> mutate(combined=case_when(
    b_start=="none" & b_end=="none" ~ "no_baseline",
    b_start==-1000 & b_end==0 ~ "baseline of -1000 - 0",
    T ~ NA
  ))
}

set_of_lollis(bc_icc, bc_cdi, bc_test_retest, bc_include)
```

```{r, fig.height=7, fig.width=8}

baseline_bc <- function(df){
  df |>  mutate(
    b_all=str_c(b_start, " -- " ,b_end) |> as.factor(),
    b_all=relevel(b_all, "none -- none")
  )
}


fix_bc_interact <- function(df){
  df |> mutate(contrast=str_replace_all(contrast, "\\)", "") |> str_replace_all("\\(", "")) |> separate(contrast, sep=" ", c("start", NA, "end", NA, NA, NA)) |> 
  mutate(b_start=str_replace(start, "b_start", ""),
         b_end=str_replace(end, "b_end", "")) 
  
}
make_model_grid_plot(bc_icc, bc_cdi, bc_test_retest, baseline_bc, "b_all", x=b_start, col=b_end, fix_function=fix_bc_interact, breaks=c(-.2, 0), limits=c(-.4,.1))
        
```

# RT

TODO FIX heat plot maybe? 

```{r rt-heat, fig.cap="Heat map of different parameter options for measuring RT. TODO note that RTs were not sampled evenly across this range, not sure what x-axis distribution should be here!", fig.width=7, fig.height=3}
rt_icc <- readRDS(here("cached_intermediates/3_rt_icc_boot.rds"))

rt_icc_meta <- rt_icc |> do_meta(c("window", "time_0", "time_end", "during", "frac", "measure"))
rt_icc_meta |>
  regroup_rt() |>
  filter(window != "1000") |>
  mutate(
    type = ifelse(type == "land", "Land RT,", "Launch RT,"),
    trimming = ifelse(trimming == "untrimmed", "", "max-shift cutoff,"),
    logged = ifelse(logged == "log", "log scale", "raw scale")
  ) |>
  ggplot(aes(y = as.character(window), fill = estimate, group = window, x = str_c(type, " ", trimming, " ", logged))) +
  geom_tile(interpolate = T) +
  coord_flip() +
  scale_fill_viridis(discrete = F, option = "magma") +
  labs(y = "RT measure", x = "Minimum RT", color = "ICC reliability")
```

unclear what the "bad" version should be 

Note that CDI comp and CDI prod is reverse goodness here!! (possibly should do something in graphs to make it easier??)
```{r, fig.height=7, fig.width=6}
rt_icc <- readRDS(here("cached_intermediates/3_rt_icc_boot.rds")) |> 
  regroup_rt() |>
  name_rt() |> filter(window<=600)

rt_cdi <- readRDS(here("cached_intermediates/3_rt_cdi_boot.rds")) |>
  regroup_rt() |>
  name_rt() |> filter(window<=600)

rt_trt <- readRDS(here("cached_intermediates/3_rt_test_retest_boot.rds")) |>
  regroup_rt() |> name_rt() |> filter(window<=600)


rt_include <- function(df){
  df |> mutate(combined=case_when(
    window==400 & trimming=="untrimmed"& logged=="log"&type=="land" ~ "400 untrimmed land, log",
    window==200 & trimming=="trim_first"& logged=="raw"&type=="first_launch" ~ "200 trimmed launch, raw",

    T ~ NA
  ))
}

set_of_lollis(rt_icc, rt_cdi, rt_trt, rt_include)
```
Note that CDI comp and CDI prod is reverse goodness here!! 

```{r, fig.height=7, fig.width=8}

baseline_rt <- function(df){
  df  |>  mutate(
    window=relevel(window, "400"),
    trimming=relevel(trimming, "untrimmed"),
    logged=relevel(logged, "log"),
    type=relevel(type, "land")
  )
}


fix_rt_interact <- function(df){

  df |> mutate(contrast=str_replace_all(contrast, "\\)", "") |> str_replace_all("\\(", "")) |> separate(contrast, sep=" ", c("trimming", "type", "window", "logged", NA, NA, NA, NA)) |> 
  mutate(window=str_replace(window, "window", "") |> as.numeric(),
        ) 
  
}
make_model_grid_plot(rt_icc, rt_cdi, rt_trt, baseline_rt, "window * trimming * logged * type", x=window, col=str_c(trimming, " ", type), facet=logged, fix_function=fix_rt_interact)
        
```

# acc trial

todo later -- can do robustness on other start/end combos!


also probably want some sort of how much data got tossed out? 
```{r, fig.height=7, fig.width=6}
trial_icc <- readRDS(here("cached_intermediates/4_acc_trial_icc_boot.rds")) |> filter(t_start==400, t_end==3000) |> select(-num_trials)
trial_cdi <- readRDS(here("cached_intermediates/4_acc_trial_cdi_boot.rds")) |> filter(t_start==400, t_end==3000)

trial_trt <- readRDS(here("cached_intermediates/4_acc_trial_test_retest_boot.rds")) |> filter(t_start==400, t_end==3000)

  trial_acc_include <- function(df){
  df |> mutate(combined=case_when(
    exclude_less_than==0 & look_both=="no_need"~ "no trial exclude",
     exclude_less_than==.5 & look_both=="ever"~ "look both at least 50%",

    T ~ NA
  ))
}

set_of_lollis(trial_icc, trial_cdi, trial_trt, trial_acc_include) 
```

```{r, fig.height=7, fig.width=8}

baseline_trial_acc <- function(df){
  df  |>  mutate(
    exclude_less_than=relevel(exclude_less_than, "0"),
    look_both=relevel(look_both, "no_need")
  )
}


fix_trial_acc_interact <- function(df){

  df |> mutate(contrast=str_replace_all(contrast, "\\)", "") |> str_replace_all("\\(", "")) |> separate(contrast, sep=" ", c("exclude_less_than", "look_both", NA, NA)) |> 
  mutate(exclude_less_than=str_replace(exclude_less_than, "exclude_less_than", "") |> as.numeric(),
        ) 
  
}
make_model_grid_plot(trial_icc, trial_cdi, trial_trt, baseline_trial_acc, "exclude_less_than * look_both", x=exclude_less_than, facet=look_both, fix_function=fix_trial_acc_interact, limits=c(-.4, .1))
        
```

# acc kid

again could try with other param combos!

again want something about how much data is getting jettisoned 
could also consider comboing with previous

```{r, fig.height=7, fig.width=6}



kid_icc <- readRDS(here("cached_intermediates/4_acc_kid_icc_boot.rds")) |> filter(t_start==400, t_end==3000, exclude_less_than==0, look_both=="no_need") |> select(-num_trials)
kid_cdi <- readRDS(here("cached_intermediates/4_acc_kid_cdi_boot.rds")) |>  filter(t_start==400, t_end==3000, exclude_less_than==0, look_both=="no_need") 

kid_trt <- readRDS(here("cached_intermediates/4_acc_kid_test_retest_boot.rds")) |>  filter(t_start==400, t_end==3000, exclude_less_than==0, look_both=="no_need") 

kid_acc_include <- function(df){
  df |> mutate(combined=case_when(
    min_trial==1 ~ "any",
     min_trial==5~ "5 trials",
    T ~ NA
  ))
}

set_of_lollis(kid_icc, kid_cdi, kid_trt, kid_acc_include) 
```

```{r, fig.height=7, fig.width=8}

baseline_kid_acc <- function(df){
  df  |>  mutate(
    min_trial=relevel(min_trial, "1")
  )
}


fix_kid_acc_interact <- function(df){

  df |> mutate(contrast=str_replace_all(contrast, "\\)", "") |> str_replace_all("\\(", "")) |> separate(contrast, sep=" ", c("min_trial", NA)) |> 
  mutate(min_trial=str_replace(min_trial, "min_trial", "") |> as.numeric(),
        ) 
  
}
make_model_grid_plot(kid_icc, kid_cdi, kid_trt, baseline_kid_acc, "min_trial", x=min_trial,  fix_function=fix_kid_acc_interact)
        
```


# kid rt

could look at other variations later 


it's RT so comp and prod are reverse -- lower is better!
```{r, fig.height=7, fig.width=6}

kid_rt_icc <- readRDS(here("cached_intermediates/4_rt_icc_boot.rds"))  |>
  regroup_rt() |>
  name_rt() |> 
  filter(window==400, trimming=="untrimmed", logged=="log", type=="land")

kid_rt_cdi <- readRDS(here("cached_intermediates/4_rt_cdi_boot.rds")) |>
  regroup_rt() |>
  name_rt() |>   filter(window==400, trimming=="untrimmed", logged=="log", type=="land")


kid_rt_trt <- readRDS(here("cached_intermediates/4_rt_test_retest_boot.rds")) |>
  filter(dataset_name != "potter_remix") |>
  regroup_rt() |>
  name_rt() |>   filter(window==400, trimming=="untrimmed", logged=="log", type=="land")


kid_rt_include <- function(df){
  df |> mutate(combined=case_when(
    min_trial==1 ~ "any",
     min_trial==5~ "5 trials",
    T ~ NA
  ))
}

set_of_lollis(kid_rt_icc, kid_rt_cdi, kid_rt_trt, kid_rt_include) 
```
```{r, fig.height=7, fig.width=8}

baseline_kid_rt <- function(df){
  df  |>  mutate(
    min_trial=relevel(min_trial, "1")
  )
}


fix_kid_rt_interact <- function(df){

  df |> mutate(contrast=str_replace_all(contrast, "\\)", "") |> str_replace_all("\\(", "")) |> separate(contrast, sep=" ", c("min_trial", NA)) |> 
  mutate(min_trial=str_replace(min_trial, "min_trial", "") |> as.numeric(),
        ) 
  
}
make_model_grid_plot(kid_rt_icc, kid_rt_cdi, kid_rt_trt, baseline_kid_rt, "min_trial", x=min_trial,  fix_function=fix_kid_rt_interact)
        
```